### 2018-12-18 paper/main.tex
new commit

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Cosmological Evidences of Dark Matter through the CMB}
\author{Lorenzo Speri}
\date{}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle

\section{Introduction}
The recent measurements of the Cosmic Microwave Background (CMB) radiation allowed us to infer the presence of Dark Matter in the Universe. In this summary we will explain qualitatively how the presence of Dark Matter influences the CMB anisotropies.

\section{}

\begin{figure}[h!]
\centering
\includegraphics[scale=1.7]{universe}
\caption{The Universe}
\label{fig:universe}
\end{figure}

\section{Conclusion}
``I always thought something was fundamentally wrong with the universe'' \citep{adams1995hitchhiker}

\bibliographystyle{plain}
\bibliography{references}
\end{document}

### 2018-12-18 presentation/main.tex
bib added

\documentclass{beamer}
%
% Choose how your presentation looks.
%
% For more themes, color themes and font themes, see:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
%
\mode<presentation>
{
  \usetheme{Madrid}      % or try Darmstadt, Madrid, Warsaw, ...
  \usecolortheme{beaver} % or try albatross, beaver, crane, ...
  \usefonttheme{serif}  % or try serif, structurebold, ...
  \setbeamertemplate{navigation symbols}{}
  \setbeamertemplate{caption}[numbered]
}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{xcolor}
\usepackage{animate}

\usepackage{physics}
\usepackage{listings}
\lstset
{
    language=[LaTeX]TeX,
    breaklines=true,
    basicstyle=\tt\scriptsize,
    %commentstyle=\color{green}
    keywordstyle=\color{blue},
    %stringstyle=\color{black}
    identifierstyle=\color{magenta},
}

\title[University of Heidelberg]{Cosmological Evidences of Dark Matter from the Cosmic Microwave Background}
\author{Lorenzo Speri}
\date{November 2, 2018}

\AtBeginSection[]
{
  \begin{frame}<beamer>
    \frametitle{Outline}
    \tableofcontents[currentsection,currentsubsection]
  \end{frame}
}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

% Uncomment these lines for an automatically generated outline.
%\begin{frame}{Outline}
%  \tableofcontents
%\end{frame}

\section{Introduction}

\begin{frame}{Cosmic Microwave Background}

\begin{center}
\animategraphics[loop,controls,width=\textwidth]{1}{something-}{0}{3}\\
%\tiny
Accurate measurements of the temperature fluctuations of the CMB\\ help  us to understand the energy-matter content of our Universe

\end{center}
\end{frame}

\begin{frame}{The best Black Body Spectrum}
\begin{figure}
   \includegraphics[height=6.5cm]{blackbody.png}
\end{figure}
$$<T_{CMB}> = 2.728 \pm 0.004 \text{ K}$$ 
\end{frame}

\begin{frame}{Dicrepancy between the expected temperature fluctuations}
At the decoupling time, the density contrast 
\[
\delta \rho = \frac{\rho - <\rho>}{<\rho>} \approx 10^{-3}
\]
If the CMB energy density $u$ were of equal magnitude, temperature fluctuations in the CMB should be of order $10^{-3}$ because
\[
u \propto T^4 \quad \Rightarrow \quad \frac{\delta u}{u} = 4 \frac{\delta T}{T}
\]
But the measured temperature fluctuations are of order $10^{-5}$ !
%It was realised later that the problem can be solved if dark matter does not electromagnetically interact, because then structures can form in the dark matter much before decoupling without leaving a direct imprint on the CMB temperature fluctuations. This is the strongest argument that dark matter should not interact electromagnetically, and probably only through the weak interaction.
\end{frame}

\section{$\Lambda$CDM model}
\begin{frame}{Assumptions of the $\Lambda$CDM model}

\begin{columns}
		\begin{column}{3cm}
			 \animategraphics[loop,controls,height=3cm]{4}{exp-}{0}{20}
			\begin{center}
				\tiny
				Spherical Harmonics
			\end{center}
		\end{column}
		\begin{column}{6cm}
			At 'enough' large scales $> 100$ Mpc, the Universe is
	\begin{itemize}
  		\item Homogeneous  
  		\item Isotropic
	\end{itemize}
		\end{column}
	\end{columns}
% class of observer that satisfies these assumption

	\vspace{0.5cm}
So the line element can be expressed as
\begin{equation*}
    \dd s^2 = g_{\mu \nu} \dd x^\mu \dd x^\nu = -c^2 \dd t^2 + a(t)^2 
    \qty( \frac{\dd r^2}{1-K r^2} + r^2 \dd \Omega ^2 )
\end{equation*}
where $a(t)$ is the scale factor and $K$ is the curvature of the Universe
\end{frame}

\begin{frame}{Friedmann Equations}
In addition, we trust Einstein's General Theory of Relativity
\begin{equation*}
    R^{\mu \nu} - \frac{1}{2}R g^{\mu \nu} + \Lambda g^{\mu \nu} = \frac{8 \pi G}{c^4} T^{\mu \nu}
\end{equation*}
\vspace{0.3cm}
Einstein’s field equations reduce to Friedmann’s equations
\begin{eqnarray}
     H^2 = \qty(\frac{\dot{a}}{a})^2 = \frac{8 \pi G \rho}{3} - \frac{K c^2}{a^2} + \frac{\Lambda  c^2}{3} \notag \\
\notag \\
     \dv{}{t}\qty{\rho c^2 a^3} + p \dv{}{t} \qty{a^3} =0 \notag
\end{eqnarray}
 where the Hubble constant is defined as $H_0 = H(t_0) = 100 h km s^{-1} Mpc^{-1} = $ and $h = 0.6727$
\end{frame}

\begin{frame}{Matter content & Cosmic Rule}

    	\begin{columns}
        	\begin{column}{0.5\textwidth}
        	    	\begin{center}
        	    	Radiation $p = \frac{\rho c^2}{3}$
        	    	$$\rho = \rho_0 a^{-4}$$
              	\end{center}

        	\end{column}
            \begin{column}{0.5\textwidth}
             \begin{center}
              Dust $p=\rho \ll \rho c^2$
              $$\rho = \rho_0 a^{-3}$$
             \end{center}
        	\end{column}
    	\end{columns}
    	\vspace{0.5cm}
    	Friedmann's equations can be rewritten using:
    	\begin{eqnarray}
    	     \Omega_R = \frac{8 \pi G \rho_R}{3 H_0 ^2} \qquad
    	     \Omega_M =  \frac{8 \pi G \rho_M}{3 H_0 ^2} \qquad
    	     \Omega_\Lambda =  \frac{\Lambda}{3 H_0 ^2} \qquad
    	     \Omega_K = -\frac{K}{a_0 ^2 H_0 ^2} \notag
    	\end{eqnarray}

    	$$
    	H^2 = H_0 ^2 \qty{\Omega_R \frac{a_0 ^4}{a^4} + \Omega_M \frac{a_0 ^3}{a^3} + \Omega_\Lambda + \Omega_K \frac{a_0 ^2}{a^2}} 
    	$$
    	At $a =a_0$ $\Rightarrow$ today, we get the Cosmic Rule: 
    	$$
    	1 = \Omega_R +  \Omega_M + \Omega_\Lambda + \Omega_K
    	$$
\end{frame}

\begin{frame}{Multipoles Decomposition}
    	\begin{columns}
		\begin{column}{4cm}
			 \animategraphics[loop,controls,width=\textwidth]{4}{multipole-}{0}{34}
			\begin{center}
				\tiny
				Spherical Harmonics
			\end{center}
		\end{column}
		\begin{column}{6cm}
			Projection of the temperature fluctuations onto another set of basis functions which are orthonormal on the sky:
			$$
			 T(\theta,\phi) = \sum_{l,m} a_{lm} Y^m _l (\theta,\phi)
			$$

			And $$C_l = \frac{1}{2l +1} \sum _{m=-l} ^l \abs{a_{lm}} ^2$$
		\end{column}
	\end{columns}

\end{frame}

\begin{frame}{Temperature Power Spectrum Planck 2015}
    \begin{figure}
   \includegraphics[height=7cm]{planck2015.jpeg}
\end{figure}
$$D_l ^{TT} = l(l+1)C_l/(2\pi)$$
\end{frame}

\begin{frame}{Temperature Power Spectrum and Angular size}
    \animategraphics[loop,controls,width=\textwidth]{2}{filter-}{0}{18}\\
    \begin{center}
        For large $l$, $
			\theta \sim 1/l
			$
    \end{center}

\end{frame}

\section{The role of the Dark Matter}

\begin{frame}{Variations of the cosmological parameters}
% we can see where the dark matter played an important role
    \begin{figure}
   \includegraphics[height=8cm]{dt_parameter_variation}
\end{figure}

\end{frame}

\begin{frame}{Variations of the Dark Matter density}
\begin{columns}
  \begin{column}{6cm}
   \animategraphics[loop,controls,height=6cm]{10}{matter_change-}{0}{27}
\end{column}
		\begin{column}{4cm}
		\begin{itemize}
		    \item Raising the dark matter density reduces the overall amplitude of the peaks
		    \item  High third peak is an indication of dark matter
		\end{itemize}

\end{column}
	\end{columns}
\end{frame}

\begin{frame}{Variations of the Baryon density}
% we can see where the dark matter played an important role
  \begin{center}

  \begin{columns}
		\begin{column}{6cm}
			 \animategraphics[loop,controls,height=6cm]{10}{baryon_change-}{0}{19}
		\end{column}
		\begin{column}{4cm}
			\begin{itemize}
			\small
			    \item Power spectrum shows baryons enhance every other peak
			    %The odd numbered acoustic peaks are enhanced in amplitude over the even numbered ones as $\Omega_B h^2$ increases
			    \item  Second peak is suppressed compared with the first and third
			    %since adding mass to a spring slows the oscillation down, adding baryons to the plasma decrease the frequency of the oscillations pushing the position of the peaks to slightly higher multipoles l
			    \item Adding baryons to the plasma decrease the frequency of the oscillations pushing the position of the peaks to slightly higher multipoles l
			\end{itemize}
		\end{column}
	\end{columns}

\end{center}
\end{frame}

\begin{frame}{Acoustic Oscillations}
At the time before recombination:
\begin{itemize}
    \item Dark Matter is randomly distributed
    \item if a portion of photon-baryon fluid is in a potential well of the dark matter, it will fall to the center of the well
    \item gravity compresses the photon-baryon fluid
    \item pressure starts to rise
    \item the pressure is sufficient to cause the fluid to expand outward
    \item the pressure drops until gravity causes the photon-baryon fluid to fall inward again
\end{itemize}
\begin{center}
    \animategraphics[loop,controls,height=3cm]{10}{plane-}{0}{7}

\end{center}
\end{frame}

\begin{frame}{Acoustic Oscillations: Simple Model}

			\animategraphics[loop,controls,width=\textwidth]{5}{hotcold-}{0}{9}

			\begin{itemize}
			    \item Quantum fluctuations from the early universe generates both density enhancements and deficits
			    \item During the inflation these quantum fluctuations had been stretched into cosmic scales
			\end{itemize}

\end{frame}

\begin{frame}{Parameters from Planck 2015}
CMB \& temperature power spectrum  $+$ nucleosynthesis analysis $\Rightarrow$ Dark-matter density.
\vspace{0.3cm}
\begin{itemize}
    \item Derk-matter density $0.2647$ $\Rightarrow$ relative error $1.6 \%$
    \vspace{0.3cm}
    \item Dark-energy density $0.6844$ $\Rightarrow$ relative error $1.3 \%$
        \vspace{0.3cm}

    \item Baryonic matter density $0.04917$ $\Rightarrow$ relative error $1.2 \%$
        \vspace{0.3cm}

    \item Radiation density $8.51 \times 10^{-5}$ $\Rightarrow$ relative error $0.6 \%$
\end{itemize}
     %\begin{figure}
   %\includegraphics[width=10cm]{table.jpg}
%\end{figure}
\end{frame}

\begin{frame}{Dark Matter matters ... for anisotropies!}
    \begin{itemize}
        \item Dark Matter interacts with the photons and matter through the gravitational potentials causing fluctuations.
        \vspace{0.5cm}
        \item Fluctuations are  responsible for anisotropy formations
        \vspace{0.5cm}
        \item The resultant fluctuations appear to the observer today as anisotropies on the sky
    \end{itemize}

\end{frame}

\begin{frame}[allowframebreaks]{References}
\nocite{*}
\bibliographystyle{plain}
\bibliography{dark_bib.bib}
\end{frame}

\end{document}

### 2018-12-20 paper/main.tex
bib added
structure 1

@@
 \section{Introduction}
-The recent measurements of the Cosmic Microwave Background (CMB) radiation allowed us to infer the presence of Dark Matter in the Universe.
+-brief thermal history of the universe and how to get to the cmb and what is it?\\
+-practical Motivation for studyinbg the cmb: nice spectrum black body spectrum: physics well know, very intense radiation\\
+which info can we get from the cmb: Big bang, maater and energy content of the universe---dark matter is a big part of the matter content it influenced the spectrum  of the CMB ---- so it played a role.\\
+-structure of the paper \\
+
+%The recent measurements of the Cosmic Microwave Background (CMB) radiation allowed us to infer the presence of Dark Matter in the Universe.
 In this summary we will explain qualitatively how the presence of Dark Matter influences the CMB anisotropies.
 
-\section{}
+\section{From the Discovery of the CMB to the Planck mission}
+\citep{bucherPhysicsCosmicMicrowave2015}
+-discovery of the cmb
+-filterng of the images
+-different missions
 
@@
 \section{Conclusion}
-``I always thought something was fundamentally wrong with the universe'' \citep{adams1995hitchhiker}
+nn
+\citep{padmanabhanDetectingDarkMatter2005}
 
 \bibliographystyle{plain}
-\bibliography{references}
+\bibliography{dark}
 \end{document}

### 2018-12-23 paper/main.tex
baryonic effect

@@
 \section{Introduction}
--brief thermal history of the universe and how to get to the cmb and what is it?\\
+-\citep{WayneHu} brief thermal history of the universe and how to get to the cmb and what is it?\\
 -practical Motivation for studyinbg the cmb: nice spectrum black body spectrum: physics well know, very intense radiation\\
@@
 \citep{bucherPhysicsCosmicMicrowave2015}
--discovery of the cmb
--filterng of the images
--different missions
+-discovery of the cmb\\
+-filterng of the images\\
+-different missions\\
+
+\section{Content of the Universe}
+\begin{itemize}
+\item Assumptions: working with the $\Lambda$CDM model
+\item General relativty
+\item Friedmann equations
+\end{itemize}
+
+\section{CMB theo analysis}
+\begin{itemize}
+\item hydrodynamics \citep{huLectureNotesCMB2008}
+page 14 eq 49 to page 17 eq 71\\
+skip doppler effect
+\item gravito acoustic oscillations page 19 up to eq 82 , justify briefly constant potential in page 20
+% if stress perturbations are negligible compared with density perturbations ( δp ≪ δρ ) then the potential will remain constant in periods where the background equation of state p/ρ is constant
+\item page 20 and 21 up to eq92 important comment 
+%The consequence is that overdense regions where Ψ is negative (potential wells) are cold spots in the effective temperature.
+\item baryonic effect
+\end{itemize}
+hydrodinamics
 

### 2018-12-23 paper/main.tex
introduction

@@
 \section{Introduction}
+Many astronomical and cosmological observations suggest that there is a missing form of matter that interacts gravitationally. 
+Therefore, scientists have proposed the existence of a new form of matter that does not interact electromagnetically but gravitationally: Dark Matter.
+Neverthless the fundamental nature of Dark Matter is not well understood, there are strong evidences for the existence of Dark Matter. 
+One of the most important evidence of the existance of Dark Matter comes from the analysis of the Cosmic Microwave Background.
+
+Since Dark Matter does not interact electromagnetically, its existence has been animatedly discussed.
+
 -\citep{WayneHu} brief thermal history of the universe and how to get to the cmb and what is it?\\
@@
 \end{itemize}
-hydrodinamics
+
+\section{Comments on the results and plots of the CMB spectrum}
 

### 2018-12-23 paper/main.tex
bib changed

@@
 Therefore, scientists have proposed the existence of a new form of matter that does not interact electromagnetically but gravitationally: Dark Matter.
-Neverthless the fundamental nature of Dark Matter is not well understood, there are strong evidences for the existence of Dark Matter. 
-One of the most important evidence of the existance of Dark Matter comes from the analysis of the Cosmic Microwave Background.
+Nevertheless the fundamental nature of Dark Matter is not well understood, there are strong evidences for the existence of Dark Matter. 
+One of the most important evidence for the existence of Dark Matter comes from the analysis of the Cosmic Microwave Background (CMB). \\
+The Cosmic Microwave Background is the electromagnetic radiation coming from the hot plasma of the early stages of the Universe.
+When the Universe, made of hot plasma, reached a temperature low enough to form stable hydrogen $e^- + p^+  \rightarrow H + \gamma$, the number density of the free electrons dropped, causing the Thomson scattering $e^- + \gamma  \rightarrow e^- + \gamma$ to be inefficient and the photons to decouple.
+They have since streamed freely through the universe and are today observed as the cosmic microwave background \citep{LecturesPdf}
 
-Since Dark Matter does not interact electromagnetically, its existence has been animatedly discussed.
-
--\citep{WayneHu} brief thermal history of the universe and how to get to the cmb and what is it?\\
 -practical Motivation for studyinbg the cmb: nice spectrum black body spectrum: physics well know, very intense radiation\\
@@
 \section{From the Discovery of the CMB to the Planck mission}
+The early Universe was made of a hot and dense plasma made that cooled down as the Universe was expanding. At $T= 100$ GeV  particles receive their masses through the Higgs mechanism
+
+-\citep{WayneHu} brief thermal history of the universe and how to get to the cmb and what is it?\\
+
 \citep{bucherPhysicsCosmicMicrowave2015}
@@
 \bibliographystyle{plain}
-\bibliography{dark}
+\bibliography{dark_1}
 \end{document}

### 2018-12-24 paper/main.tex
from the discovery of the cmb to Planck mission

--- 2018-12-23 paper/main.tex
@@
 \date{}
-
+\usepackage{hyperref}
 \usepackage{natbib}
 \usepackage{graphicx}
+% ---- Maths -------
+\usepackage{amsmath}
+\usepackage{amsthm}
+% ---- Links -------
+\usepackage{hyperref}
+
+%  ---- my commands -------
+\newcommand{\bea}{\setlength{\jot}{10pt}\begin{eqnarray*}}
+\newcommand{\eea}{\end{eqnarray*}}
+\newcommand{\beq}{\begin{equation}}
+\newcommand{\eeq}{\end{equation}}
+\newcommand{\bpsi}{\bar{\psi}}
+\newcommand{\dslash}{\slashed{\partial}}
+\newcommand{\Dslash}{\slashed{D}}
+\newcommand{\Lagr}{\mathcal{L}}
+\newcommand{\cpp}{\texttt{C++} } 
+\newcommand{\mpi}{\texttt{MPI} } 
+\newcommand{\de}{\nu}
+\newcommand{\T}{\text{TT}}
+\newcommand{\h}{\mathscr{H}}
+\newcommand{\ten}{\mathscr{T}}
 
@@
 \section{Introduction}
--\citep{WayneHu} brief thermal history of the universe and how to get to the cmb and what is it?\\
+Many astronomical and cosmological observations suggest that there is a missing form of matter that interacts gravitationally. 
+In order to explain such observations, scientists have proposed the existence of Dark Matter, a new form of matter that does not interact electromagnetically but gravitationally.
+However, the fundamental nature of Dark Matter is not well understood yet, and whether Dark Matter is truly a new form of matter or the effect of new laws of gravity is still matter of debate.\\
+One of the most compelling evidence for the existence of Dark Matter comes from the analysis of the Cosmic Microwave Background (CMB).
+In this paper we explain how the  analysis of the CMB is linked to the energy-matter content of our Universe, and, within this framework, we study the role of Dark Matter.
+The aim of this paper is to give a short and concise overview of the cosmological evidence of Dark Matter given by the observations of the CMB.
+\\
+
+The Cosmic Microwave Background is the electromagnetic radiation coming from the hot plasma of the early stages of the Universe.
+When the Universe, made of hot plasma, reached a temperature low enough to form stable hydrogen $e^- + p^+  \rightarrow H + \gamma$ the number density of the free electrons dropped, causing the Thomson scattering $e^- + \gamma  \rightarrow e^- + \gamma$ to be inefficient and the photons to decouple.
+They have since streamed freely through the universe and are today observed as the Cosmic Microwave Background \citep{LecturesPdf}.\\
+
+\subsection{to be put in the paper or at the end}
 -practical Motivation for studyinbg the cmb: nice spectrum black body spectrum: physics well know, very intense radiation\\
@@
 \section{From the Discovery of the CMB to the Planck mission}
-\citep{bucherPhysicsCosmicMicrowave2015}
--discovery of the cmb\\
--filterng of the images\\
--different missions\\
+
+\begin{figure}
+\includegraphics[width=\textwidth]{Horn_Antenna.jpeg}
+\caption{The 15 meter Holmdel horn antenna at Bell Telephone Laboratories in Holmdel, New Jersey.
+(By NASA - Great Images in NASA Description, Public Domain, \url{https://commons.wikimedia.org/w/index.php?curid=6463768})}
+\end{figure}
+
+In 1965 Arno Penzias and Robert Wilson published the paper: \emph{A measurement of excess antenna temperature at
+4080 Mc/s}, where they reported the measurements of an isotropic, unpolarized, and free from seasonal variations excess noise temperature
+\citep{penziasMeasurementExcessAntenna1965}. 
+When Penzias and Wilson first measured serendipitously this strong signal, they did everything they could think of to reduce “noise” in their system. 
+They even shooed away a pair of pigeons that had roosted in the antenna and cleaned up they later called “the usual white dielectric” generated by pigeons \citep{RydenIntroCosmoPdf}.
+However, the signal remained. 
+Robert Dicke and his research group at Princeton University explained such signal as the relic of an early, hot, dense, and opaque state of the universe\footnote{the existence of the cosmic background radiation had actually been predicted by the physicist George Gamow and his colleagues in 1948} \citep{bucherPhysicsCosmicMicrowave2015}
+. \\
+This discovery of the CMB created a big excitement and a new era of cosmology began.
+Measuring the CMB spectrum and its deviation from the black body spectrum was the new challange.
+Many experimental efforts have been carried out to measure accurately the fluctuations of Cosmic Microwave Backgrund from its average temperature $T = 2.7$ K, we will discuss only few of them.
+\\
+First of all, the photons of the CMB can be absorbed by the Earth's atmosphere, because the energy per CMB photon (approximately $\sim 6 \times 10 ^{-4}$ eV) is comparable to the energy of vibration or rotation for a small molecule (of water for instance).
+In fact, microwaves with wavelengths shorter than $\lambda \sim 3$ cm are strongly absorbed by water molecules \citep{RydenIntroCosmoPdf}.
+This problem could be overcomed by observing the CMB in different bands and from locations where the humidity is low.
+However, the best way to meseaure the CMB spectrum is to use satellites.\\
+The first sattellite that was launched to observe the CMB was COBE. 
+It did provide a convincing first detection of the CMB anisotropy, and it played a crucial role in determining the viability of the different cosmological models at that time.
+\\
+After that, WMAP and PLanck space missions  increased the accuracy of the measurements Figure (\ref{cobe_wmap_planck}).
+Nevertheless the satellites improved their accuracy, many other sources of noise were encountered such as the light coming from the center of our galaxy, other stars and other objects in the universe, in addition to the relative motion of the satellite with respect to the CMB (Figure (\ref{cobe_map})).\\
+Finally, observations and statistical analysis showed that the CMB spectrum is close to a black body spectrum up to fluctuations of order of $10^{-5}$ K (Figure (\ref{cobe_blackbody})).\\
+% maybe last sentence in the introduction with the image
+
+\begin{figure}
+\centering
+    \textbf{CMB spectrum}\par\medskip
+\centering
+   {\includegraphics[height=8cm]{blackbody.png}}
+\caption{}
+\label{cobe_blackbody}
+\end{figure}
+
+\begin{figure}
+\centering
+    \textbf{The Cosmic Microwave Background anisotropies measured by COBE, WMAP and Planck}\par\medskip
+\centering
+   {\includegraphics[width=.45\textwidth]{cobe_wmap_planck.jpg}}
+
+\caption{The COBE, WMAP and Planck missions measured the CMB anisotropies with increasing accuracy.
+COBE, the first CMB satellite, measured fluctuations to scales of 7$^\circ$.
+WMAP was able to measure resolutions down to 0.3$^\circ$ in five different frequency bands, with Planck measuring all the way down to just 5 arcminutes (0.07$^\circ$) in nine different frequency bands in total.
+(NASA/COBE/DMR; NASA/WMAP SCIENCE TEAM; ESA AND THE PLANCK COLLABORATION)}
+\label{cobe_wmap_planck}
+\end{figure}
+
+\begin{figure}
+\centering
+    \textbf{Orbits of different  configurations of BBH}\par\medskip
+\centering
+\includegraphics[scale =0.3]{mono_di_cobe}
+\caption{The microwave sky as seen by the COBE DMR (differential microwave radiometer) instrument.
+The top panel shows the microwave sky as seen on a linear tem- perature scale including zero.
+No anisotropies are visible in this image, because the CMB monopole at 2.725K dominates.
+In the middle panel, the monopole component has been subtracted.
+Apart from some slight contamination from the galaxy near the equator (corre- sponding to the plane of our Galaxy), one sees only a nearly perfect dipole pattern, owing to our peculiar motion with respect to the rest frame defined by the CMB.
+In the bottom panel, both the monopole and dipole components have been removed.
+Except for the galactic contamination around the equator, one sees the cosmic microwave background anisotropy along with some noise.
+(Credit: NASA/COBE Science Team)}
+\label{cobe_map}
+\end{figure}
 
 \section{Content of the Universe}
+The General Theory of Relativity is the best theory of gravity that we have, so far. So,  
 \begin{itemize}
@@
 \end{itemize}
-hydrodinamics
 
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=1.7]{universe}
-\caption{The Universe}
-\label{fig:universe}
-\end{figure}
+\section{Comments on the results and plots of the CMB spectrum}
 

### 2018-12-24 paper/main.tex
new section started

@@
 \date{}
-\usepackage{hyperref}
+%\usepackage{hyperref}
 \usepackage{natbib}
@@
 % ---- Links -------
-\usepackage{hyperref}
+%\usepackage{hyperref}
+% citation color
+\usepackage[colorlinks=true,citecolor=blue]{hyperref}
 
@@
 which info can we get from the cmb: Big bang, maater and energy content of the universe---dark matter is a big part of the matter content it influenced the spectrum  of the CMB ---- so it played a role.\\
--structure of the paper \\
+-\textbf{structure of the paper} \\
 
@@
 \centering
-    \textbf{CMB spectrum}\par\medskip
+    \textbf{Cosmic Microwave Background  Spectrum}\par\medskip
 \centering
-   {\includegraphics[height=8cm]{blackbody.png}}
+   {\includegraphics[height=8cm]{blackbody}}
 \caption{}
@@
 \section{Content of the Universe}
+The experimental results from the observations of the Cosmic Microwave Background provide important details about energy-matter content of the Universe. 
+We now need to set the theoretical framework we want to use to analyze the observations of the CMB.\\
+We assume that the observable properties of the Universe are isotropic and there is not a preferred direction.
+Therefore, the Universe is assumed to be homogenous and isotropic at enough large scales $> 100$ Mpc, at least up to the observable universe.\\
+Another important assumption is that there exists a class of observers at rest with respect to the Cosmic Microwave Background \citep{bartelmannStandardModelCosmology}.
+These observers do not see the dipole pattern typical of a moving observer with respect with the CMB.
+For instance the Earth is not at rest with respect to the CMB as we can notice from the second panel in Figure (\ref{cobe_map}).\\
+
+The best theory of gravity that can tell us accurately how the different components of the Universe evolved is the General Theory of Relativity, so far.
+Therefore, we assume the correctnes of the General Theory of Relativity.
+
+ the energy-matter contentandis carried out using different 
 The General Theory of Relativity is the best theory of gravity that we have, so far. So,  

### 2018-12-27 paper/main.tex
section content of the universe

--- 2018-12-24 paper/main.tex
@@
 \usepackage{amsthm}
+\usepackage{physics}
 % ---- Links -------
-\usepackage{hyperref}
+%\usepackage{hyperref}
+% citation color
+\usepackage[colorlinks=true,citecolor=blue]{hyperref}
+% for twnsore
+\usepackage{tensind}
+\tensordelimiter{:}
 
@@
 The aim of this paper is to give a short and concise overview of the cosmological evidence of Dark Matter given by the observations of the CMB.
+We are interested in providing few but fundamental ingredients to understand the importance of the CMB for Dark Matter to a reader that is not familiar with the topic.
 \\
+
+\subsection{The Cosmic Microwave Background in few lines}
 
@@
 
-\subsection{to be put in the paper or at the end}
 -practical Motivation for studyinbg the cmb: nice spectrum black body spectrum: physics well know, very intense radiation\\
 which info can we get from the cmb: Big bang, maater and energy content of the universe---dark matter is a big part of the matter content it influenced the spectrum  of the CMB ---- so it played a role.\\
--structure of the paper \\
+-\textbf{structure of the paper} \\
+--The experimental results from the observations of the Cosmic Microwave Background provide important details about energy-matter content of the Universe.
 
@@
 
-\begin{figure}
+\begin{figure}[h]
 \centering
-    \textbf{CMB spectrum}\par\medskip
+    \textbf{Cosmic Microwave Background  Spectrum}\par\medskip
 \centering
-   {\includegraphics[height=8cm]{blackbody.png}}
+   {\includegraphics[height=8cm]{blackbody}}
 \caption{}
@@
 
-\begin{figure}
+\begin{figure}[h]
 \centering
@@
 \end{figure}
+\pagebreak
 
 \section{Content of the Universe} 
-The General Theory of Relativity is the best theory of gravity that we have, so far. So,  
-\begin{itemize}
-\item Assumptions: working with the $\Lambda$CDM model
-\item General relativty
-\item Friedmann equations
-\end{itemize}
+It is often said that our Universe is made up of $68.8$\% of Dark Energy, and $26.8 $\% by Dark Matter and $4.9 $\% of ordinary matter, but what do we really mean by that?\\
+In this section we explain where the components of our Universe (Dark Matter, baryonic matter, Dark Energy, curvature)  arise from and how they are related with each others. 
+The assumptions and the theoretical framework that we are going to explain will be then used to analyze the observations of the CMB.\\
+We assume that the observable properties of the Universe are isotropic and there is not a preferred direction. 
+Therefore, the Universe is assumed to be homogenous and isotropic at enough large scales $> 100$ Mpc, at least up to the observable universe.\\
+Another important assumption is that there exists a class of observers at rest with respect to the Cosmic Microwave Background \citep{bartelmannStandardModelCosmology}.
+Let us clarify this concept. 
+After subtracting the average temperature of the CMB from its spectrum, a moving observer with respect with the CMB will see a dipole pattern, where the blue-shifted photons come from the direction the observer is moving toward to and the red-shifted photons from the opposite direction.
+Since Earth is not at rest with respect to the CMB, the satellite COBE measured the dipole pattern showed in the second panel in Figure (\ref{cobe_map}).\\
+Given these assumptions, the most general metric $g_{\mu \nu}$ satisfying homogeneity and isotropy is the Friedmann–Lemaître–Robertson–Walker (FLRW) metric written here in terms of the invariant geodesic distance $\dd s ^2 = g_{\mu \nu} \dd x^{\mu} \dd x^{\nu}$:
+\begin{equation}
+\label{metric}
+\dd s ^2 = -\dd t^2 + a^2 (t) \qty( \frac{1}{1-k \, r^2} \dd r^2 + r^2 \dd \Omega ^2 )  
+\end{equation}
+where $k$ is the spatial curvature and $a(t)$ is the scale factor (we set the light speed $c=1$).
+Notice that the FLRW metric has $g_{0 i}=0$ due to the isotropy.
+\\ % comments on the redshift, metric, what spatially flat means
+If we assume the correctnes of the General Theory of Relativity, we can use the Einstein's field equations
+\begin{equation}
+\label{einstein_eq}
+R_{\mu \nu} - \dfrac{1}{2} R \, g _{\mu \nu} + \Lambda g_{\mu \nu}= 8 \pi G \, T_{\mu \nu}
+\end{equation}
+in order to evolve the FLRW metric.
+The Einstein's field equations relate how the geometry of spacetime (left hand side) changes with the presence of masses and energy (right hand side).
+The most general fluid consistent with the assumption of homogeneity and isotropy is a perfect fluid, one in which an observer comoving with the fluid would see the universe around it as isotropic \citep{garcia-bellidoAstrophysicsCosmology2000}.
+Therefore, the energy-momentum tensor $T_{\mu \nu}$ can be written as
+\begin{equation}
+\label{energy-momentum-tensor}
+T^{\mu \nu } = (p + \rho)u ^{\mu} u^{\nu}+p g^{\mu \nu} 
+\end{equation}
+where $\rho$ and $p$ are, respectively, the mass density and the pressure of the fluid.\\
+Solving (\ref{einstein_eq}) for $\mu= 0=\nu$ using the above definition (\ref{energy-momentum-tensor}), gives us the Friedmann equation:
+\begin{equation}
+\label{firedmann_eq}
+\begin{split}
+H^2 = \qty(\frac{\dot{a}}{a})^2 = \dfrac{8 \pi G}{3} \rho -\dfrac{k}{a^2} + \frac{\Lambda}{3}
+\end{split}
+\end{equation}
+where $\dot{a}$ is the time derivative of the scale factor.\\
+And the conservation of energy momentum tensor $\nabla_\mu T^{\mu \nu} =0 $ becomes:
+\beq
+\label{energy_cons}
+\dv[]{}{t}\qty(\rho a^3) + p \dv[]{}{t} \qty(a^3)  = 0
+\eeq
+Solving this for matter $\rho_m << p_m$ (or \emph{dust}) and for radiation $\rho_r = p_r/3$ gives
+\begin{equation}
+\begin{split}
+\rho_m = \rho_{m 0} a^{-3} \hspace{1.5cm} \rho_r = \rho_{r 0} a^{-4} \notag
+\end{split}
+\end{equation}
+where $\rho_{m 0}$ and $\rho_{r 0}$ are the matter density and radiation density evaluated today $t = t_0$, $a(t_0) = a_0 =1$.\\
+We now rewrite equation (\ref{firedmann_eq}) as
+\begin{equation}
+H ^2 = H_0 ^2 \qty[
+\dfrac{8 \pi G}{3 H_0 ^2} \rho_{m 0} a^{-3}+
+\dfrac{8 \pi G}{3 H_0 ^2} \rho_{r 0} a^{-4}+ 
+\dfrac{-k}{H_0 ^2} a^{-2} + \dfrac{\Lambda}{3 H_0 ^2}
+]
+\end{equation}
+where we defined $H_0 = H(t_0)$.\\
+\beq
+\Omega_\Lambda = \dfrac{\Lambda}{3} \qquad \Omega_k = -  \dfrac{k}{H_0 ^2}
+\\
+\Omega_m = \dfrac{8 \pi G}{3 H_0 ^2} \rho_{m 0} \qquad \Omega_r =\dfrac{8 \pi G}{3 H_0 ^2} \rho_{r 0}
+\eeq
+evaluating the Friedmann equation (\ref{firedmann_eq}) today we obtain the cosmic sum rule
+\begin{equation}
+\label{cosmic_rule}
+\Omega_{\Lambda} + \Omega_{m} + \Omega_k + \Omega_{r} = 1
+\end{equation}
 
 \section{CMB theo analysis}
+
 \begin{itemize}

### 2019-01-05 paper/main.tex
hydrodynamics

@@
 
-\begin{figure}[h]
+\begin{figure}
 \centering
@@
 \end{figure}
-\pagebreak
+
+\newpage
 
@@
 where $\dot{a}$ is the time derivative of the scale factor.\\
-And the conservation of energy momentum tensor $\nabla_\mu T^{\mu \nu} =0 $ becomes:
+And the conservation of energy momentum tensor $\nabla_\mu T^{\mu 0} =0 $ becomes:
 \beq
@@
 \eeq
+Solving for radiation $\rho = p/3$
+\[
+\dot{\rho}  + 4 \frac{ \dot{a}}{a} \rho =0
+\]
+ And solving for matter $\rho << p$
+ \[
+ \dot{\rho}  + 3 \frac{ \dot{a}}{a} \rho =0
+ \]
 Solving this for matter $\rho_m << p_m$ (or \emph{dust}) and for radiation $\rho_r = p_r/3$ gives
@@
 \dfrac{-k}{H_0 ^2} a^{-2} + \dfrac{\Lambda}{3 H_0 ^2}
-]
+] \notag
 \end{equation}
@@
 \beq
-\Omega_\Lambda = \dfrac{\Lambda}{3} \qquad \Omega_k = -  \dfrac{k}{H_0 ^2}
-\\
+\Omega_\Lambda = \dfrac{\Lambda}{3} \qquad \Omega_k = -  \dfrac{k}{H_0 ^2} \qquad
 \Omega_m = \dfrac{8 \pi G}{3 H_0 ^2} \rho_{m 0} \qquad \Omega_r =\dfrac{8 \pi G}{3 H_0 ^2} \rho_{r 0}
@@
 
-\section{CMB theo analysis}
+\section{Acoustic Oscillations}
+The Cosmic Microwave Background is the image of the fluctuations of a dense and hot fluid made of matter (baryonic and dark) and radiation.
+Before the release of the CMB at $z > 1100$ the electromagnetic radiation is firmly coupled (both energetically and kinetically) to the baryons and it is possible to describe the behavior of such a system by using the equations of relativistic hydrodynamics and the Einstein's field equations (\ref{einstein_eq}).
+The full general-relativistic description of the photon-matter fluid requires a long derivation that can be found here [BAUMANN].\\
+So, we show how the acoustic oscillations arise from a simple non-relativistic model of a ideal fluid under the effect of a gravitational potwntial $\phi$.
+We assume that there is a set of fields \\
+Derivation from Bartelmann
 

### 2019-02-19 paper/main.tex
phenomenology of the cmb

--- 2018-12-27 paper/main.tex
@@
 \tensordelimiter{:}
+
+% for comments
+\usepackage{verbatim}
 
@@
 \section{Introduction}
-Many astronomical and cosmological observations suggest that there is a missing form of matter that interacts gravitationally. 
+Many astronomical and cosmological observations suggest that there is a missing form of matter that interacts gravitationally with baryonic matter. 
 In order to explain such observations, scientists have proposed the existence of Dark Matter, a new form of matter that does not interact electromagnetically but gravitationally.
-However, the fundamental nature of Dark Matter is not well understood yet, and whether Dark Matter is truly a new form of matter or the effect of new laws of gravity is still matter of debate.\\
+The fundamental nature of Dark Matter is not well understood yet, and whether Dark Matter is truly a new form of matter or the effect of new laws of gravity is still matter of debate.\\
 One of the most compelling evidence for the existence of Dark Matter comes from the analysis of the Cosmic Microwave Background (CMB).
-In this paper we explain how the  analysis of the CMB is linked to the energy-matter content of our Universe, and, within this framework, we study the role of Dark Matter.
+In this paper we explain how the analysis of the CMB is linked to the energy-matter content of our Universe, and we study the role of Dark Matter on the power spectrum of the CMB within the $\Lambda$CDM model.
 The aim of this paper is to give a short and concise overview of the cosmological evidence of Dark Matter given by the observations of the CMB.
@@
 The Cosmic Microwave Background is the electromagnetic radiation coming from the hot plasma of the early stages of the Universe.
-When the Universe, made of hot plasma, reached a temperature low enough to form stable hydrogen $e^- + p^+  \rightarrow H + \gamma$ the number density of the free electrons dropped, causing the Thomson scattering $e^- + \gamma  \rightarrow e^- + \gamma$ to be inefficient and the photons to decouple.
+As the Universe was expanding, it cooled down to a temperature low enough to form stable hydrogen $e^- + p^+  \rightarrow H + \gamma$.
+The number density of the free electrons dropped with the expansion causing the Thomson scattering $e^- + \gamma  \rightarrow e^- + \gamma$ to be inefficient and the photons to decouple.
 They have since streamed freely through the universe and are today observed as the Cosmic Microwave Background \citep{LecturesPdf}.\\
-
+The Cosmic Microwave Background is ideal for studying the content of our Universe, because it is the best measured Planck spectrum that we know.\\
+Since we know very well the 
 -practical Motivation for studyinbg the cmb: nice spectrum black body spectrum: physics well know, very intense radiation\\
@@
 -\textbf{structure of the paper} \\
---The experimental results from the observations of the Cosmic Microwave Background provide important details about energy-matter content of the Universe.
+--The experimental results from the observations of the Cosmic Microwave Background provide important details about energy-matter content of the Universe.\\
+\paragraph{sctructure}
+We first give an historical overview of the discovery and measurements of the CMB, then we discuss the main assumptions of the $\Lambda$CDM model and the link between the content of our universe and the cosmological model.
+Afterwards, the phenomenology of the hot plasma is explained with a simplified treatment in order to understand the power spectrum of the CMB.
+We conclude with the discussion of the cmb power specctrum and the role of dark matter.
 
@@
 \label{metric}
-\dd s ^2 = -\dd t^2 + a^2 (t) \qty( \frac{1}{1-k \, r^2} \dd r^2 + r^2 \dd \Omega ^2 )  
+\dd s ^2 = -c ^2 \dd t^2 + a^2 (t) \qty( \frac{1}{1-k \, r^2} \dd r^2 + r^2 \dd \Omega ^2 )  
 \end{equation}
-where $k$ is the spatial curvature and $a(t)$ is the scale factor (we set the light speed $c=1$).
+where $k$ is the spatial curvature and $a(t)$ is the scale factor.
 Notice that the FLRW metric has $g_{0 i}=0$ due to the isotropy.
@@
 \label{einstein_eq}
-R_{\mu \nu} - \dfrac{1}{2} R \, g _{\mu \nu} + \Lambda g_{\mu \nu}= 8 \pi G \, T_{\mu \nu}
+R_{\mu \nu} - \dfrac{1}{2} R \, g _{\mu \nu} + \Lambda g_{\mu \nu}= \dfrac{8 \pi G}{c^4} \, T_{\mu \nu}
 \end{equation}
@@
 \label{energy-momentum-tensor}
-T^{\mu \nu } = (p + \rho)u ^{\mu} u^{\nu}+p g^{\mu \nu} 
+T^{\mu \nu } = (p + \rho c^2)u ^{\mu} u^{\nu}+p g^{\mu \nu} 
 \end{equation}
@@
 \begin{split}
-H^2 = \qty(\frac{\dot{a}}{a})^2 = \dfrac{8 \pi G}{3} \rho -\dfrac{k}{a^2} + \frac{\Lambda}{3}
+H^2 = \qty(\frac{\dot{a}}{a})^2 = \dfrac{8 \pi G}{3} \rho -\dfrac{k \, c^2}{a^2} + \frac{\Lambda \, c^2}{3}
 \end{split}
@@
 where $\dot{a}$ is the time derivative of the scale factor.\\
-And the conservation of energy momentum tensor $\nabla_\mu T^{\mu \nu} =0 $ becomes:
+And the conservation of energy momentum tensor $\nabla_\mu T^{\mu 0} =0 $ becomes:
 \beq
 \label{energy_cons}
-\dv[]{}{t}\qty(\rho a^3) + p \dv[]{}{t} \qty(a^3)  = 0
+\dv[]{}{t}\qty(\rho c^2 a^3) + p \dv[]{}{t} \qty(a^3)  = 0
 \eeq
+Solving for radiation $\rho c^2 = p/3$
+\[
+\dot{\rho}  + 4 \frac{ \dot{a}}{a} \rho =0
+\]
+ And solving for matter $\rho c^2 << p$
+ \[
+ \dot{\rho}  + 3 \frac{ \dot{a}}{a} \rho =0
+ \]
 Solving this for matter $\rho_m << p_m$ (or \emph{dust}) and for radiation $\rho_r = p_r/3$ gives
@@
 \dfrac{8 \pi G}{3 H_0 ^2} \rho_{r 0} a^{-4}+ 
-\dfrac{-k}{H_0 ^2} a^{-2} + \dfrac{\Lambda}{3 H_0 ^2}
-]
+\dfrac{-k \, c^2}{H_0 ^2} a^{-2} + \dfrac{\Lambda \, c^2}{3 H_0 ^2}
+] \notag
 \end{equation}
@@
 \beq
-\Omega_\Lambda = \dfrac{\Lambda}{3} \qquad \Omega_k = -  \dfrac{k}{H_0 ^2}
-\\
+\Omega_\Lambda = \dfrac{\Lambda c^2}{3} \qquad \Omega_k = -  \dfrac{k c^2}{H_0 ^2} \qquad
 \Omega_m = \dfrac{8 \pi G}{3 H_0 ^2} \rho_{m 0} \qquad \Omega_r =\dfrac{8 \pi G}{3 H_0 ^2} \rho_{r 0}
@@
 
-\section{CMB theo analysis}
+\section{Phenomenology of the Fluctuations}
+The Cosmic Microwave Background is the image of the fluctuations of a dense and hot fluid made of matter and radiation.
+Before the release of the CMB at $z > 1100$ the electromagnetic radiation is firmly coupled (both energetically and kinetically) to the baryons and it is possible to describe the behavior of such a system by using solving the equations of relativistic hydrodynamics and the Einstein's field equations (\ref{einstein_eq}) with small density $\delta \rho$, pressure $\delta p$ and gravitational potential perturbations $\delta \Phi$.
+The full general-relativistic description of the photon-matter fluid requires a complicated treatment[BAUMANN].
+However, it is possible to qualitatively discuss the phenomena occurring in the CMB fluid and the effects on the temperature fluctuations $\Theta = \delta T / T_0$.
+\subsection{Sachs-Wolfe effect}
+As a consequence of the Einstein's equivalence principle, photons that escape from a gravitational field are redshifted.
+If we consider the fluctuations of the CMB on large scales, the photons that tries to escape from the gravitational well created by matter are redshifted.
+
+\subsection{Acoustic oscillations}
+At the time of recombination
+Dark Matter is randomly distributed
+if a portion of photon-baryon fluid is in a potential well of the dark matter, it will fall to the center of the well
+gravity compresses the photon-baryon fluid
+pressure starts to rise
+the pressure is sufficient to cause the fluid to expand outward
+the pressure drops until gravity causes the photon-baryon fluid to fall inward again
+
+\subsection{Damping}
+The temperature fluctuations are damped due to collisions between the baryons and the photons that dissipate energy, and the expansion of the universe.
+
+\begin{comment}
+    This text will not be displayed.
+
+ by starting from the continuity and Euler equation for a photon fluid with  number density $n$, energy density $u$ and pressure $p$:
+\begin{equation}
+\label{hydro}
+\dot{n} + n_0 \vec{\nabla} \cdot \vec{v} = 0 \qquad
+\dot{\vec{v}} = - c^2 \dfrac{\vec{\nabla} \delta p}{p_0 + u_0} - \vec{\nabla} \delta \Phi
+\end{equation}
+where $v$ is the streaming velocity of the perturbations and the subscript $_0$ indicates the background average values of th correspondent quantities.\\
+For a photon gas we know that
+\begin{equation}
+n \propto T ^3 \qquad u \propto T^4 \qquad p  = \dfrac{u}{3}
+\end{equation}
+So, the temperature fluctuations are related to the number density, energy density and pressure as follow:
+\begin{equation}
+\dfrac{\delta n}{n_0} = 3 \Theta \qquad
+\dfrac{\delta u}{u_0} = 4 \Theta = \dfrac{\delta p}{p_0}
+\end{equation}
+We can rewrite eq.(\ref{hydro}) in terms of the temperature fluctuations:
+\begin{equation}
+\dot{\Theta} + \nabla \cdot \vec{v} = 0 \qquad \dot{\vec{v}} = - c^2 \vec{\nabla} \Theta - \vec{\nabla} \delta \Phi
+\end{equation}
+where we used $p_0 + u_0 = 4 p_0$
 
@@
 \end{itemize}
+\end{comment}
 

### 2019-02-20 paper/main.tex
last section

@@
 \usepackage[utf8]{inputenc}
-
+\usepackage[a4paper, total={6in, 8in}]{geometry}
 \title{Cosmological Evidences of Dark Matter through the CMB}
@@
 The fundamental nature of Dark Matter is not well understood yet, and whether Dark Matter is truly a new form of matter or the effect of new laws of gravity is still matter of debate.\\
-One of the most compelling evidence for the existence of Dark Matter comes from the analysis of the Cosmic Microwave Background (CMB).
+One of the most compelling evidence for the existence of Dark Matter is given by the analysis of the Cosmic Microwave Background (CMB).
 In this paper we explain how the analysis of the CMB is linked to the energy-matter content of our Universe, and we study the role of Dark Matter on the power spectrum of the CMB within the $\Lambda$CDM model.
@@
 \subsection{The Cosmic Microwave Background in few lines}
-
 The Cosmic Microwave Background is the electromagnetic radiation coming from the hot plasma of the early stages of the Universe.
-As the Universe was expanding, it cooled down to a temperature low enough to form stable hydrogen $e^- + p^+  \rightarrow H + \gamma$.
+As the Universe was expanding, the hot plasma cooled down to a temperature low enough to form stable hydrogen $e^- + p^+  \rightarrow H + \gamma$.
 The number density of the free electrons dropped with the expansion causing the Thomson scattering $e^- + \gamma  \rightarrow e^- + \gamma$ to be inefficient and the photons to decouple.
 They have since streamed freely through the universe and are today observed as the Cosmic Microwave Background \citep{LecturesPdf}.\\
-The Cosmic Microwave Background is ideal for studying the content of our Universe, because it is the best measured Planck spectrum that we know.\\
+The Cosmic Microwave Background appears to us as the best measured Planck spectrum that we know.\\
 Since we know very well the 
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{Horn_Antenna.jpeg}
+\begin{center}
+\includegraphics[width=0.7\textwidth]{Horn_Antenna.jpeg}
 \caption{The 15 meter Holmdel horn antenna at Bell Telephone Laboratories in Holmdel, New Jersey.
 (By NASA - Great Images in NASA Description, Public Domain, \url{https://commons.wikimedia.org/w/index.php?curid=6463768})}
+\end{center}
+
 \end{figure}
@@
 \centering
-   {\includegraphics[width=.45\textwidth]{cobe_wmap_planck.jpg}}
+   {\includegraphics[width=.75\textwidth]{cmb1.jpg}}
 
@@
 the pressure is sufficient to cause the fluid to expand outward
-the pressure drops until gravity causes the photon-baryon fluid to fall inward again
+the pressure drops until gravity causes the photon-baryon fluid to fall inward again\\
+Gravity tries to compress the fluid in potential wells.
+Photon pressure resists compression resulting in acoustic oscillations
+System is equivalent to a mass on a spring falling under gravity
+What is doing the pushing that compresses the fluid? Gravity.
+
+The photon-baryon fluid is sitting in the gravitational potential wells that are the seeds of structure in the universe.
+As gravity tries to compress the fluid, radiation pressure resists resulting in acoustic oscillations.
+Because it acts to resist compression, we will represent the radiation pressure abstractly as springs.
+Likewise we will represent the inertia of the fluid, or loosely speaking its mass (really energy density), as massive balls falling under gravity:\\
+
+Modes caught at extrema of their oscillations become the peaks in the CMB power spectrum.
+They form a harmonic series based on the distance sound can travel by recombination, called the sound horizon.
+The first peak represents the mode that compressed once inside potential wells before recombination, the second the mode that compressed and then rarefied, the third the mode that compressed then rarefied then compressed, etc
 
 \subsection{Damping}
-The temperature fluctuations are damped due to collisions between the baryons and the photons that dissipate energy, and the expansion of the universe.
+The temperature fluctuations are damped due to collisions between the baryons and the photons that dissipate energy, and the expansion of the universe.\\
+The damping scale provides another standard ruler for the curvature test
+The physical scale of the damping depends on the baryon density through the mean free path
+And the matter density through the time available for the photons to random walk.
+If we can calibrate the distance CMB photons random walk during recombination, we have another standard ruler for the angular diameter distance test of the spatial curvature of the universe.
+Remember that we measure its angular scale in the power spectrum itself.
 
+Alternatively, if we know the curvature of the universe we can infer the physical distance the photons travel.
+In the standard model, the physical distance depends only on the baryon density and the dark matter density (matter-radiation ratio).
+Since all three (curvature, baryons density and matter radiation) are measured by the positions and heights of the peaks themselves, the damping tail provides a beautiful consistency test for the standard model.
+
+Let's see how that works.
+
+Microphysically, the distance photons can travel is related to a random walk process.
+Remember that the photons have a certain mean free path in the baryons defined as the average distance the photon travels before Thomson scattering off a free electron:\\
+Raising the number of baryons, decreases the mean free path and hence shortens the distance photons can travel at recombination.
+Finally the full distance also depends on the amount of time the photons have to random walk and hence the age of the universe at recombination.
+Remember that the age is determined by the dark matter density.
+Mathematically, the length is roughly the geometric mean of the mean free path and the distance light can travel without obstruction (the horizon scale).
 \begin{comment}
@@
 \section{Comments on the results and plots of the CMB spectrum}
+We have seen in section 3 how general relativity and the density parameters  characterize the content of our Universe,  in section 4 the dynamics of the CMB photons is affected by matter.
+We want to link the previous theoretical results to the observations of the temperature fluctuations of the CMB sky.\\
+The spherical harmonics $Y^{m} _{l} (\theta, \phi)$ compose a set of orthonormal functions on the sky.\\
+So if $T(\theta,\phi)$ is the temperature at position $(\theta,\phi)$, it is possible to decompose the temperature into a series:
+\begin{equation}
+T(\theta, \phi) = \sum _{l, m} a_{lm} Y^{m} _l (\theta, \phi)
+\end{equation}
+Due to the orthonormality of the spherical harmonics
+\begin{equation}
+a_{lm} = \int _0 ^{2 \pi} \dd \phi \int _0  ^{\pi} \dd \theta \,
+\sin \theta \, T(\theta, \phi) \, Y^{m} _l (\theta, \phi)
+ \end{equation}
+ We define the power spectrum of the temperature map as 
+ \begin{equation}
+ C_l = \dfrac{1}{2l+1} \sum _{m=-l} ^{l} |a_{lm}|^2
+ \end{equation}
+The measured temperature power spectrum is shown in Figure(\ref{temp_pow_spect})
+%
+%
+%
+\begin{figure}
+\includegraphics[width=0.9\textwidth]{planck2018}
+\caption{Planck 2018 temperature power spectrum. $\mathcal{D}^{TT}_l = l(l+1)C_l$ (arXiv:1807.06209v1)}
+\label{temp_pow_spect}
+\end{figure}
+%
+%
+%
+The Sachs-Wolfe effect is dominant on large scales, i.e. small l.\\
+The first peak is at $l \approx 200$ and the  acoustic oscillations take place.
+The damping effect is evident for $l>10^{3}$.\\
 
+\subsection{Dark Energy and Curvature}
+
+Position of peaks mainly sensitive to curvature
+Shapes fixed by the physical density of matter and baryons
+Missing or "dark energy" plays a small roll in the position of peaks
+As advertised, the position of that first peak in the power spectrum of the anisotropies, and indeed all of the peaks, depend sensitively on the spatial curvature of the universe.
+As the curvature of the universe decreases (and in fact becomes negative in the yellow curve below)\\
+the peaks move to smaller angles (higher multipole l) while preserving their shape.
+Cosmologists fraction of the critical density in matter Omegam so that as 1-Omegamincreases from zero, the universe becomes increasingly negatively curved if there is no other forms of "missing energy" that we've missed in our accounting.
+
+Caveats:
+
+In the blue curve, we assume that there is indeed a form of "missing" or dark energy in a cosmological constant that makes the universe flat despite a sub-critical density of matter.
+We see that the positions mainly care about the curvature of the universe but there is a small shift to larger angular scales (lower multipoles) through the introduction of a cosmological constant.
+This is because the cosmological constant produces a small change in the distance light can travel since recombination, a fact that is related to its well known effect on the age of the universe.
+
+Note that in the above figure we assume that the physical density of the matter (Omegamh2) is fixed.
+This is different from saying its fraction of the critical density (Omegam) is fixed since the Hubble constant (h), or expansion rate today, enters into the definition of the critical density.
+Given our current uncertainties about the physical density of the matter, the distance that sound can travel by recombination is currently uncertain, a fact related to the matter's effect on the age of the universe at recombination.
+Likewise we have assumed that the physical density of the baryons  (Omegabh2) is fixed.
+Baryons lower the speed of sound in the medium and hence also affect the distance sound can travel.
+Luckily both of these quantities dramatically change the shape of the peaks as we shall see.
+They will be measured once the higher peaks are detected and will no longer confuse the measurement of the curvature.
+As it turns out, the sound horizon is not a standard ruler but rather a standardizeable ruler.
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{curvature_de}
+\caption{}
+
+\end{center}
+\label{DE_curv}
+\end{figure}
+
+\subsection{Dark Matter and Baryons}
+Baryons (or ordinary matter) load down the photon-baryon plasma and add inertial (and gravitational) mass to the oscillating system.
+
+Their effect on the acoustic peaks is easy to understand.
+Remember what happens when you add mass to a spring and let it fall in the gravitational field of the Earth.
+With more mass loading the spring, it falls further before pulled back by the spring.
+On the other hand, it rebounds to the same position it started from.
+
+Since the odd numbered (first, third, fifth...) acoustic peaks are associated with how far the plasma "falls" into gravitational potential wells (how much the plasma compresses), they are enhanced by an increase in the amount of baryons in the universe.
+The even numbered peaks (second, fourth, sixth) are associated with how far the plasma "rebounds" (how much the plasma rarefies).
+Thus with the addition of baryons the odd peaks are enhanced over the even peaks.
+For example, baryons make the first acoustic peak much larger than the second.
+The more baryons the more the second peak is relatively suppressed.
+\par
+
+%http://background.uchicago.edu/~whu/intermediate/baryons2.html
+\paragraph{image}
+Power spectrum shows baryons enhance every other peak.
+Second peak is suppressed compared with the first and third
+Additional effects on the peak position and damping yield consistency checks
+When we do the full calculation of the power spectrum, the basic physics of a mass on the spring appears as advertised.
+The odd numbered acoustic peaks in the power spectrum are enhanced in amplitude over the even numbered ones as we increase the baryon density of the universe.\\
+Note: Cosmologists label the baryon density in terms of its fraction of the critical density Wbtimes the Hubble constant squared (in units of 100 km/s/Mpc) to get something proportional to the physical density of the baryons.]
+
+There are two other related effects due to the baryons:  since adding mass to a spring slows the oscillation down, adding baryons to the plasma decrease the frequency of the oscillations pushing the position of the peaks to slightly higher multipoles l.
+
+Baryons also affect the way the sound waves damp and hence how the power spectrum falls off at high multipole moment lor small angular scales as we will see later.
+
+The many ways that baryons show up in the power spectrum imply that the power spectrum has many independent checks on the baryon density of the universe.
+The baryon density is a quantity that the CMB can measure to exquisite precision.
+
+\paragraph{dark matter}
+Second peak is observed to be substantially lower than first peak
+Dark baryons of at least the big-bang nucleosynethesis density required
+Although we cannot yet claim that the second peak is as precisely measured as the first, we can say that (assuming it exists!) it is definitely of lower amplitude than the first:\\
+The current data indicate that the baryon density is around Omegabh2=0.02 This value is interesting since it is also the baryon density inferred from the abundance of deuterium at high redshift in quasar absorption lines and the theory of big-bang nucleosynthesis.
+We now have an additional and independent line of evidence that there are missing baryons in the universe - i.e.
+that most the baryons are not in stars.
+Once the second and higher peaks are definitively measured, CMB constraints on the baryon density will sharpen considerably (ultimately to a few percent accuracy).
+Needless to say it will be interesting to see how these comparisons shape up as the data improve.
+\paragraph{dark}
+Raising the dark matter density reduces the overall amplitude of the peaks.
+Lowering the dark matter density eliminates the baryon loading effect so that a high third peak is an indication of dark matter.
+With three peaks, its effects are distinct from the baryons
+Measuring the dark matter density resolves the main ambiguity in the curvature measurement
+As advertised the acoustic peaks in the power spectrum are sensitive to the dark matter density in the universe.
+(Formally, the matter to radiation ratio but the radiation density is fixed in the standard model.)\\
+As we raise the physical density of the dark matter, Wmh2, the driving effect goes away at a given peak such that its amplitude decreases.
+Although this effect changes the heights of all the peaks, it is only separable from the baryonic effects with at least three peaks.
+Note that decreasing the matter density also affects the baryon loading since the dark matter potential wells go away leaving nothing for the baryons to fall into.
+Having a third peak that is boosted to a height comparable to or exceeding the second peak is an indication that dark matter dominated the matter density in the plasma before recombination.
+Note that the self-gravity of the photons and baryons still plays a role in the first and second peaks so that the third peak is the cleanest test of this behavior.
+
+Notice also that the location of the peaks, and that of the first peak in particular, changes as we change the dark matter density.
+The matter to radiation ratio also controls the age of the universe at recombination and hence how far sound can travel relative to how far light travels after recombination.
+This is the leading order ambiguity in the measurement of the spatial curvature of the universe.
+We see here that that ambiguity will be resolved when at least three peaks are precisely measured.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{baryon_m}
+\caption{aa}
+\end{center}
+\label{DM_bar}
+\end{figure}
 \section{Conclusion}

### 2019-02-20 paper/main.tex
introduction

@@
 \section{Introduction}
-Many astronomical and cosmological observations suggest that there is a missing form of matter that interacts gravitationally with baryonic matter. 
-In order to explain such observations, scientists have proposed the existence of Dark Matter, a new form of matter that does not interact electromagnetically but gravitationally.
-The fundamental nature of Dark Matter is not well understood yet, and whether Dark Matter is truly a new form of matter or the effect of new laws of gravity is still matter of debate.\\
-One of the most compelling evidence for the existence of Dark Matter is given by the analysis of the Cosmic Microwave Background (CMB).
-In this paper we explain how the analysis of the CMB is linked to the energy-matter content of our Universe, and we study the role of Dark Matter on the power spectrum of the CMB within the $\Lambda$CDM model.
-The aim of this paper is to give a short and concise overview of the cosmological evidence of Dark Matter given by the observations of the CMB.
-We are interested in providing few but fundamental ingredients to understand the importance of the CMB for Dark Matter to a reader that is not familiar with the topic.
-\\
-
-\subsection{The Cosmic Microwave Background in few lines}
+Many astronomical and cosmological observations suggest that, by using the General Theory of Relativity, there is an invisible form of matter that exerts a gravitational pull on baryonic matter. 
+In order to explain such observations, scientists have proposed the existence of Dark Matter, a new form of matter that does not interact electromagnetically and, therefore, it appears invisible to us.
+The fundamental nature of Dark Matter is not well understood yet, and whether Dark Matter is truly a new form of matter or the consequence of new laws of gravity is still matter of debate.\\
+One of the most compelling evidence for the existence of Dark Matter is given by the analysis of the Cosmic Microwave Background (CMB).\\
 The Cosmic Microwave Background is the electromagnetic radiation coming from the hot plasma of the early stages of the Universe.
-As the Universe was expanding, the hot plasma cooled down to a temperature low enough to form stable hydrogen $e^- + p^+  \rightarrow H + \gamma$.
-The number density of the free electrons dropped with the expansion causing the Thomson scattering $e^- + \gamma  \rightarrow e^- + \gamma$ to be inefficient and the photons to decouple.
-They have since streamed freely through the universe and are today observed as the Cosmic Microwave Background \citep{LecturesPdf}.\\
-The Cosmic Microwave Background appears to us as the best measured Planck spectrum that we know.\\
-Since we know very well the 
--practical Motivation for studyinbg the cmb: nice spectrum black body spectrum: physics well know, very intense radiation\\
-which info can we get from the cmb: Big bang, maater and energy content of the universe---dark matter is a big part of the matter content it influenced the spectrum  of the CMB ---- so it played a role.\\
--\textbf{structure of the paper} \\
---The experimental results from the observations of the Cosmic Microwave Background provide important details about energy-matter content of the Universe.\\
-\paragraph{sctructure}
+As the Universe was expanding, it cooled down to a temperature low enough to form stable hydrogen $e^- + p^+  \rightarrow H + \gamma$ (Recombination). 
+As the number density of the free electrons dropped with the expansion, the Thomson scattering $e^- + \gamma  \rightarrow e^- + \gamma$ became inefficient and the photons have since streamed freely through the universe in all directions and they are today observed as the Cosmic Microwave Background \citep{LecturesPdf}.\\
+The Cosmic Microwave Background appears to us as the best measured Planck spectrum that we know with fluctuations of order $10 ^{-5}$ around the average temperature $T_{CMB} =2.725$ K.
+The fluctuations are extremely important because they contain the crucial information about the primordial plasma and its content. 
+In fact, during the early stages of the Universe, the photons were interacting with baryonic matter, which in turn was interacting gravitationally with dark matter.
+Thus, the observations of the CMB fluctuations are linked to the energy-matter content of our Universe and dark matter.\\
+The aim of this paper is to give a short and concise overview of the physics of the CMB and the cosmological evidence of Dark Matter through the analysis of the CMB fluctuations within the $\Lambda$CDM model assumptions.
+We are interested in providing few but fundamental tools to understand the importance of the CMB for Dark Matter.\\
 We first give an historical overview of the discovery and measurements of the CMB, then we discuss the main assumptions of the $\Lambda$CDM model and the link between the content of our universe and the cosmological model.
 Afterwards, the phenomenology of the hot plasma is explained with a simplified treatment in order to understand the power spectrum of the CMB.
-We conclude with the discussion of the cmb power specctrum and the role of dark matter.
+We conclude with the discussion of the CMB temperature power spectrum and the role of dark matter.
 

### 2019-02-21 paper/main.tex
sachs-wolfe effect

@@
 \usepackage[utf8]{inputenc}
-\usepackage[a4paper, total={6in, 8in}]{geometry}
+\usepackage{geometry}
+ \geometry{
+ a4paper,
+ bottom=40mm
+ %total={170mm,257mm},
+ %left=20mm,
+ %top=20mm,
+ }
  \title{Cosmological Evidences of Dark Matter through the CMB}
@@
 
+\vspace{3cm}
 \section{Introduction}
@@
 In this summary we will explain qualitatively how the presence of Dark Matter influences the CMB anisotropies.
-
+\pagebreak
 \section{From the Discovery of the CMB to the Planck mission}
-
+%
+%
+%
 \begin{figure}
@@
 (By NASA - Great Images in NASA Description, Public Domain, \url{https://commons.wikimedia.org/w/index.php?curid=6463768})}
+\label{antenna}
 \end{center}
-
 \end{figure}
-
+%
+%
+%
+In the 1960s Penzias and Wilson measured an isotropic and constant with time strong signal coming from the sky by using a horn-reflector radio antenna (Figure(\ref{antenna})). 
+They tried everything they could do to reduce the “noise” in their system, but the signal remained.\\
 In 1965 Arno Penzias and Robert Wilson published the paper: \emph{A measurement of excess antenna temperature at
@@
 \citep{penziasMeasurementExcessAntenna1965}.
-When Penzias and Wilson first measured serendipitously this strong signal, they did everything they could think of to reduce “noise” in their system. 
-They even shooed away a pair of pigeons that had roosted in the antenna and cleaned up they later called “the usual white dielectric” generated by pigeons \citep{RydenIntroCosmoPdf}.
-However, the signal remained. 
-Robert Dicke and his research group at Princeton University explained such signal as the relic of an early, hot, dense, and opaque state of the universe\footnote{the existence of the cosmic background radiation had actually been predicted by the physicist George Gamow and his colleagues in 1948} \citep{bucherPhysicsCosmicMicrowave2015}
+The explanation of that signal was given by Robert Dicke and his research group at Princeton University: such signal as the relic of an early, hot, dense, and opaque state of the universe\footnote{The existence of the cosmic background radiation had actually been predicted by the physicist George Gamow and his colleagues in 1948} \citep{bucherPhysicsCosmicMicrowave2015}
 . \\
-This discovery of the CMB created a big excitement and a new era of cosmology began.
+The discovery of the CMB created a big excitement and a new era of cosmology began.
 Measuring the CMB spectrum and its deviation from the black body spectrum was the new challange.
-Many experimental efforts have been carried out to measure accurately the fluctuations of Cosmic Microwave Backgrund from its average temperature $T = 2.7$ K, we will discuss only few of them.
 \\
@@
 In fact, microwaves with wavelengths shorter than $\lambda \sim 3$ cm are strongly absorbed by water molecules \citep{RydenIntroCosmoPdf}.
-This problem could be overcomed by observing the CMB in different bands and from locations where the humidity is low.
+This problem could be overcomed by observing the CMB in different bands and from locations where the atmospheric humidity is low, at high altitudes and at low temperatures.
 However, the best way to meseaure the CMB spectrum is to use satellites.\\
@@
 \\
-After that, WMAP and PLanck space missions  increased the accuracy of the measurements Figure (\ref{cobe_wmap_planck}).
+After that, WMAP and PLanck space missions  increased the accuracy of the measurements Figure (\ref{cobe_wmap_planck}).\\
+The COBE, WMAP and Planck missions measured the CMB anisotropies with increasing accuracy.
+COBE, the first CMB satellite, measured fluctuations to scales of 7$^\circ$.
+WMAP was able to measure resolutions down to 0.3$^\circ$ in five different frequency bands, with Planck measuring all the way down to just 5 arcminutes (0.07$^\circ$) in nine different frequency bands in total.\\
 Nevertheless the satellites improved their accuracy, many other sources of noise were encountered such as the light coming from the center of our galaxy, other stars and other objects in the universe, in addition to the relative motion of the satellite with respect to the CMB (Figure (\ref{cobe_map})).\\
@@
 \centering
-   {\includegraphics[height=8cm]{blackbody}}
+   {\includegraphics[height=7cm]{blackbody}}
 \caption{}
@@
 \centering
-   {\includegraphics[width=.75\textwidth]{cmb1.jpg}}
+   {\includegraphics[width=.65\textwidth]{cmb1.jpg}}
 
-\caption{The COBE, WMAP and Planck missions measured the CMB anisotropies with increasing accuracy.
-COBE, the first CMB satellite, measured fluctuations to scales of 7$^\circ$.
-WMAP was able to measure resolutions down to 0.3$^\circ$ in five different frequency bands, with Planck measuring all the way down to just 5 arcminutes (0.07$^\circ$) in nine different frequency bands in total.
-(NASA/COBE/DMR; NASA/WMAP SCIENCE TEAM; ESA AND THE PLANCK COLLABORATION)}
+\caption{(NASA/COBE/DMR; NASA/WMAP SCIENCE TEAM; ESA AND THE PLANCK COLLABORATION)}
 \label{cobe_wmap_planck}
@@
 \centering
-    \textbf{Orbits of different  configurations of BBH}\par\medskip
+    \textbf{The CMB sky measured by COBE}\par\medskip
 \centering
@@
 It is often said that our Universe is made up of $68.8$\% of Dark Energy, and $26.8 $\% by Dark Matter and $4.9 $\% of ordinary matter, but what do we really mean by that?\\
-In this section we explain where the components of our Universe (Dark Matter, baryonic matter, Dark Energy, curvature)  arise from and how they are related with each others. 
+In this section we explain the meaning of these parameters and what is Universe made up of. 
 The assumptions and the theoretical framework that we are going to explain will be then used to analyze the observations of the CMB.\\
@@
 Let us clarify this concept.
+The CMB appears as an homogeneous map at temperature $T=2.7$ K as shown in the first panel of Figure(\ref{cobe_map}).
 After subtracting the average temperature of the CMB from its spectrum, a moving observer with respect with the CMB will see a dipole pattern, where the blue-shifted photons come from the direction the observer is moving toward to and the red-shifted photons from the opposite direction.
 Since Earth is not at rest with respect to the CMB, the satellite COBE measured the dipole pattern showed in the second panel in Figure (\ref{cobe_map}).\\
-Given these assumptions, the most general metric $g_{\mu \nu}$ satisfying homogeneity and isotropy is the Friedmann–Lemaître–Robertson–Walker (FLRW) metric written here in terms of the invariant geodesic distance $\dd s ^2 = g_{\mu \nu} \dd x^{\mu} \dd x^{\nu}$:
+In addition we assume that space-time is described by a metric theory of gravity, and we treat space-time as a 4-dimensional manifold characterized by the metric tensor $g_{\mu \nu}$.
+The most general metric $g_{\mu \nu}$ satisfying homogeneity and isotropy assumptions is the Friedmann – Lemaître – Robertson – Walker (FLRW) metric written here in terms of the invariant geodesic distance $\dd s ^2 = g_{\mu \nu} \dd x^{\mu} \dd x^{\nu}$:
 \begin{equation}
@@
 \end{equation}
-where $k$ is the spatial curvature and $a(t)$ is the scale factor.
-Notice that the FLRW metric has $g_{0 i}=0$ due to the isotropy.
+where $k$ is the space curvature and it determines the geometry of the spatial dimensions, elliptical, Euclidean or hyperbolic for $k>0$, $k=0$ or $k<0$.
+The space curvature determines in which kind of three dimensional space we live in and how angles are measured.\\
+The scale factor $a(t)$ determines how the distances scale with the evolution of the Universe.
+The propagation condition of light is $ds^2 =0$, which implies that the light with frequency $\nu$ and the wavelength $\lambda$ is red- or blueshifted by the same amount as space expands or shrinks:
+\begin{equation}
+\dfrac{\nu_{emitted}}{\nu_{observed}} = \dfrac{\lambda_{emitted}}{\lambda_{observed}} = 1 + \dfrac{\lambda_{emitted}-\lambda_{observed}}{\lambda_{observed}}=1+z= \dfrac{a(t_{emitted})}{a(t_{observed})}
+\end{equation}
+\\
+Notice that the FLRW metric has $g_{0 i}=0$ due to the isotropy and the two parameters $a(t)$ and $k$ are the only allowed to preserve our assumptions, all the others parameter that we can introduce can be absorbed in these two.
 \\ % comments on the redshift, metric, what spatially flat means
@@
 \end{equation}
-in order to evolve the FLRW metric.
-The Einstein's field equations relate how the geometry of spacetime (left hand side) changes with the presence of masses and energy (right hand side).
+in order to understand how spacetime evolves by using the FLRW metric.
+The Einstein's field equations relate how the geometry of spacetime (left hand side) changes with the presence of masses and energy (right hand side).\\
 The most general fluid consistent with the assumption of homogeneity and isotropy is a perfect fluid, one in which an observer comoving with the fluid would see the universe around it as isotropic \citep{garcia-bellidoAstrophysicsCosmology2000}.
@@
 where $\rho$ and $p$ are, respectively, the mass density and the pressure of the fluid.\\
-Solving (\ref{einstein_eq}) for $\mu= 0=\nu$ using the above definition (\ref{energy-momentum-tensor}), gives us the Friedmann equation:
+Solving (\ref{einstein_eq})and using the above definition (\ref{energy-momentum-tensor}) (which is a rather long and tedious derivation), gives us the Friedmann equation:
 \begin{equation}
@@
 \begin{split}
-H^2 = \qty(\frac{\dot{a}}{a})^2 = \dfrac{8 \pi G}{3} \rho -\dfrac{k \, c^2}{a^2} + \frac{\Lambda \, c^2}{3}
+H^2 = \qty(\frac{\dot{a}}{a})^2 &= \dfrac{8 \pi G}{3} \rho -\dfrac{k \, c^2}{a^2} + \frac{\Lambda \, c^2}{3} \\
+\vspace{1.5cm}
+\dfrac{\ddot{a}}{a} &= -\dfrac{4 \pi G}{3} \qty(\rho + 3 \dfrac{p}{c^2} ) +  \frac{\Lambda \, c^2}{3}
 \end{split}
 \end{equation}
-where $\dot{a}$ is the time derivative of the scale factor.\\
-And the conservation of energy momentum tensor $\nabla_\mu T^{\mu 0} =0 $ becomes:
+where  $\dot{}$  represents the time derivative.\\
+The first Friedmann equation tells us how the Hubble parameter$H(t)$, i.e. the expansion rate,  evolves according to what is contained in our Universe.
+The second Friedmann equation tells how the Universe accelerates.\\
+In order to solve the system we need another equation: the equation of state $p = w \rho$ that relates the the pressure and the mass density.\\
+%
+%
+%
+% comment
+%\begin{comment}
+By using the conservation of energy momentum tensor $\nabla_\mu T^{\mu 0} =0 $ becomes:
 \beq
@@
 \eeq
+%\end{comment}
+%
+%
+%
+% comment
+\begin{comment}
 Solving for radiation $\rho c^2 = p/3$
@@
  \]
-Solving this for matter $\rho_m << p_m$ (or \emph{dust}) and for radiation $\rho_r = p_r/3$ gives
+ \end{comment}
+Solving this for dust (a name for non-relativistic matter) $\rho_m c^2 << p_m$ and for radiation $\rho_r c^2 = p_r/3$ gives
 \begin{equation}
@@
 \end{equation}
-where $\rho_{m 0}$ and $\rho_{r 0}$ are the matter density and radiation density evaluated today $t = t_0$, $a(t_0) = a_0 =1$.\\
-We now rewrite equation (\ref{firedmann_eq}) as
+where $\rho_{m 0}$ and $\rho_{r 0}$ are the matter density and radiation density evaluated today $t = t_0$, $a(t_0) = a_0 =1$.
+The above result is somehow intuitive because the normal non-relativistic matter is "diluted" as the the spatial distances $a^3$  increase with the expansion of the Universe, i.e.
+the number of particles per unit volume decreases with the expansion.
+The energy density of radiation $u = \rho_r c^2 $ decreases with the power of four because photons experience not only the dilution due to the spatial expansion but their frequencies, accordingly their energies, decreased by the streching of spacetime.\\
+We now rewrite the first Friedmann equation as
 \begin{equation}
@@
 \end{equation}
-where we defined $H_0 = H(t_0)$.\\
+where we defined $H_0 = H(t_0)$.
+The above equation tells us that in the limit of $a \rightarrow 0$ the expansion rate and the evolution of the early Universe was determined by radiation.
+In the other limit the future of the Universe is determined by the cosmological constant $\Lambda$.
+We have not specified the nature of the cosmological constant, up to now it has been trated as a possible parameter that can be added to the Einstein's field equations(\ref{einstein_eq}).
+\\
+If we define the density parameters as:
 \beq
-\Omega_\Lambda = \dfrac{\Lambda c^2}{3} \qquad \Omega_k = -  \dfrac{k c^2}{H_0 ^2} \qquad
-\Omega_m = \dfrac{8 \pi G}{3 H_0 ^2} \rho_{m 0} \qquad \Omega_r =\dfrac{8 \pi G}{3 H_0 ^2} \rho_{r 0}
+\Omega_{\Lambda 0} = \dfrac{\Lambda c^2}{3 H_0 ^2} \qquad \Omega_{k0} = -  \dfrac{k c^2}{H_0 ^2} \qquad
+\Omega_{m0} = \dfrac{8 \pi G}{3 H_0 ^2} \rho_{m 0} \qquad \Omega_{r0} =\dfrac{8 \pi G}{3 H_0 ^2} \rho_{r 0}
 \eeq
-evaluating the Friedmann equation (\ref{firedmann_eq}) today we obtain the cosmic sum rule
+ and evaluating the Friedmann equation (\ref{firedmann_eq}) today $a(t_0) =a_0 =1$ we obtain the cosmic sum rule
 \begin{equation}
 \label{cosmic_rule}
-\Omega_{\Lambda} + \Omega_{m} + \Omega_k + \Omega_{r} = 1
+\Omega_{\Lambda 0} + \Omega_{m 0} + \Omega_{k 0} + \Omega_{r 0} = 1
 \end{equation}
+So the experimental measurements of these parameters must add up to one.
+We will see in the next sections how the CMB power spectrum puts constraints on these parameters and tell use that there is a form of matter that we cannot wee.
 
 \section{Phenomenology of the Fluctuations}
-The Cosmic Microwave Background is the image of the fluctuations of a dense and hot fluid made of matter and radiation.
-Before the release of the CMB at $z > 1100$ the electromagnetic radiation is firmly coupled (both energetically and kinetically) to the baryons and it is possible to describe the behavior of such a system by using solving the equations of relativistic hydrodynamics and the Einstein's field equations (\ref{einstein_eq}) with small density $\delta \rho$, pressure $\delta p$ and gravitational potential perturbations $\delta \Phi$.
-The full general-relativistic description of the photon-matter fluid requires a complicated treatment[BAUMANN].
-However, it is possible to qualitatively discuss the phenomena occurring in the CMB fluid and the effects on the temperature fluctuations $\Theta = \delta T / T_0$.
+The Cosmic Microwave Background fluctuations were produced when radiation and matter were interacting in the early stage of the Universe.
+Before the release of the CMB at $z > 1100$ the electromagnetic radiation is firmly coupled (both energetically and kinetically) to the baryons.
+The behavior of such a system can be solved by using the equations of relativistic hydrodynamics and the Einstein's field equations (\ref{einstein_eq}) with small perturbations of density $\delta \rho$, pressure $\delta p$ and gravitational potential  $\delta \Phi$.
+Perturbations of different scales propagate as sound waves through the plasma until they are frozen at the time of recombination and they appear to us as temperature fluctuations $\Theta = \delta T /T$ in the CMB map.
+For a photon gas we know that the temperature fluctuations are related to the number density $n$, energy density $u = \rho c^2$ and pressure $p$ as follow:
+\begin{equation}
+n \propto T ^3 \rightarrow \dfrac{\delta n}{n_0} = 3 \Theta \qquad \qquad \qquad
+ u \propto T^4  \qquad p  = \dfrac{u}{3} \rightarrow \dfrac{\delta u}{u_0} = 4 \Theta = \dfrac{\delta p}{p_0} \notag
+\end{equation}
+Solving the full general-relativistic description of the photon-matter fluid requires a long and complicated treatment [BAUMANN], so we use instead an analogy with the most favourite model of a physicist: the harmonic oscillator\footnote{As in every analogy in physics, the phenomena are not the same.
+A mass on a spring is not the same as a relativistic fluid perturbation in an expanding 4-dimensional manifold, but the analogy is very helpful for the understanding and the equations are not that different (in first approximation)}.\\
+All kinds of perturbations are proportional to the temperature fluctuations $\Theta$, so we  can associate the fluctuations to the displacement $x$ of spring-mass system. 
+The fluctuations of the primordial fluid can be characteried by a typical scale $\lambda =2 \pi /k$ of oscillation/propagation that could depends on the local gravitational pull, pressure or properties.
+In addition, they are damped due to the expasion of the Universe and due to collisions, and ultimately they feel a constant gravitational pull from the overall fluid.
+By analogy with the mass-spring system we analyze the fluctuations at different scales by solving the well known equation:
+\begin{equation}
+m\ddot{x} = - k x - \eta \dot{x} - m g \qquad \rightarrow \qquad \ddot{x} + 2 \gamma \dot{x} + \omega_k ^2 x + g =0
+\end{equation}
+where $k$ is linked to the scale of oscillations $\omega_k ^2 = k/m$, $\eta$ to the damping ($2 \gamma = \eta /m$), $g$ to the constant gravitational pull of the overall system and $m$ the inertia of the perturbation.
+The general solution of the differential equation is 
+\begin{equation}
+x = x_0 e^{i \, \omega t} - \dfrac{g \, m}{k} \qquad \qquad \omega = i \gamma \pm \sqrt{ \omega_k ^2 - \gamma^2}
+\end{equation}
+We will discuss how with this simple model we can obtain some of the features of the CMB power spectrum at different scales.
+
 \subsection{Sachs-Wolfe effect}
+In the harmonic oscillator model for very small $k$ the mass experiences only the gravitational pull of the overdensities $x \approx - g m/k$ and it does not oscillate.
+We can compare the x displacement of the spring with the size of the oscillation $\lambda$
+\[
+\dfrac{x}{\lambda} \approx -\dfrac{g m}{\lambda k} \dfrac{\lambda}{\lambda} = -\dfrac{g \lambda}{\lambda^2 \omega_k ^2}
+\]
+Notice that the numerator is the gravitational potential of a uniform field and the denominator is proportional to the speed of the oscillations.\\
+In the photon-baryon fluid, perturbation modes of very large scales (large $\lambda$, very small $k$) do not have the time to complete an entire oscillation before recombination and they are influenced only by the gravitational potential of the overdensities.
 As a consequence of the Einstein's equivalence principle, photons that escape from a gravitational field are redshifted.
-If we consider the fluctuations of the CMB on large scales, the photons that tries to escape from the gravitational well created by matter are redshifted.
+If we consider the fluctuations of the CMB on large scales, the photons that tries to escape from the gravitational well created by matter are redshifted according to the so-called Sachs-Wolfe effect.
+The theoretical result from the relativistic derivation gives a temperature fluctuation $\Theta = -\delta \Phi /(3c^2)$.
+The Sachse Wolfe effect takes into account an additional effect that cannot be explained with the simple harmonic oscillator model and it arises from the time dilation due to the expansion of the Universe.
 
@@
 where $v$ is the streaming velocity of the perturbations and the subscript $_0$ indicates the background average values of th correspondent quantities.\\
-For a photon gas we know that
-\begin{equation}
-n \propto T ^3 \qquad u \propto T^4 \qquad p  = \dfrac{u}{3}
-\end{equation}
+
 So, the temperature fluctuations are related to the number density, energy density and pressure as follow:
@@
 We want to link the previous theoretical results to the observations of the temperature fluctuations of the CMB sky.\\
+The temperature fluctuations are projected in the sky map and they appear to us as anisotropies in the sky map tempearature.
+
 The spherical harmonics $Y^{m} _{l} (\theta, \phi)$ compose a set of orthonormal functions on the sky.\\

### 2019-02-22 paper/main.tex
section 5

@@
 \usepackage{verbatim}
+% wrapping figures
+\usepackage{wrapfig}
 
@@
 %\begin{comment}
-By using the conservation of energy momentum tensor $\nabla_\mu T^{\mu 0} =0 $ becomes:
+By using the conservation of energy momentum tensor $\nabla_\mu T^{\mu 0} =0 $ yields:
 \beq
@@
 A mass on a spring is not the same as a relativistic fluid perturbation in an expanding 4-dimensional manifold, but the analogy is very helpful for the understanding and the equations are not that different (in first approximation)}.\\
-All kinds of perturbations are proportional to the temperature fluctuations $\Theta$, so we  can associate the fluctuations to the displacement $x$ of spring-mass system. 
-The fluctuations of the primordial fluid can be characteried by a typical scale $\lambda =2 \pi /k$ of oscillation/propagation that could depends on the local gravitational pull, pressure or properties.
-In addition, they are damped due to the expasion of the Universe and due to collisions, and ultimately they feel a constant gravitational pull from the overall fluid.
+All kinds of perturbations are proportional to the temperature fluctuations $\Theta$, so we  can associate the fluctuations to the displacement $x$ of spring-mass system from its equilibrium.
+Let us build the analogy.
+The fluctuations of the primordial fluid can be characterized by a typical scale $\lambda = 2 \pi /k$ of oscillation/propagation that could depends on the local gravitational pull, pressure or other properties.
+It is important to stress that $k$ is not a wavevector, but it acts as it was. 
+In fact, the $k$ parameter will represent the strength of the spring.
+If $k$ is small, the spring is loose and it  oscillates over large scales $\lambda$, analogously the oscillations of the fluctuations will have a large wavelength. \\ 
+In addition, fluctuations are damped due to the expasion of the Universe and due to collisions, and ultimately they feel a constant gravitational pull from the overall fluid.
 By analogy with the mass-spring system we analyze the fluctuations at different scales by solving the well known equation:
@@
 \end{equation}
-We will discuss how with this simple model we can obtain some of the features of the CMB power spectrum at different scales.
+We will discuss the overall behavior of the photon-baryon fluid at different scales $\lambda$ by studying the solutions of the harmonic oscillator for different $k$.
 
 \subsection{Sachs-Wolfe effect}
-In the harmonic oscillator model for very small $k$ the mass experiences only the gravitational pull of the overdensities $x \approx - g m/k$ and it does not oscillate.
-We can compare the x displacement of the spring with the size of the oscillation $\lambda$
-\[
-\dfrac{x}{\lambda} \approx -\dfrac{g m}{\lambda k} \dfrac{\lambda}{\lambda} = -\dfrac{g \lambda}{\lambda^2 \omega_k ^2}
-\]
-Notice that the numerator is the gravitational potential of a uniform field and the denominator is proportional to the speed of the oscillations.\\
+In the harmonic oscillator model for very small $k$ the mass experiences only the gravitational pull of the overdensities $x \approx - g m/k$ and it does not oscillate.\\
 In the photon-baryon fluid, perturbation modes of very large scales (large $\lambda$, very small $k$) do not have the time to complete an entire oscillation before recombination and they are influenced only by the gravitational potential of the overdensities.
@@
 
-\subsection{Acoustic oscillations}
-At the time of recombination
-Dark Matter is randomly distributed
-if a portion of photon-baryon fluid is in a potential well of the dark matter, it will fall to the center of the well
-gravity compresses the photon-baryon fluid
-pressure starts to rise
-the pressure is sufficient to cause the fluid to expand outward
-the pressure drops until gravity causes the photon-baryon fluid to fall inward again\\
-Gravity tries to compress the fluid in potential wells.
-Photon pressure resists compression resulting in acoustic oscillations
-System is equivalent to a mass on a spring falling under gravity
-What is doing the pushing that compresses the fluid? Gravity.
+\subsection{Acoustic Oscillations and Damping}
+\begin{wrapfigure}{r}{6cm}
+\centering
+%\begin{figure}
+\includegraphics[scale=0.5]{baryonspring}
+%\end{figure}
+\end{wrapfigure}
+Let us consider again the harmonic oscillator model in the case of $\omega_k > \gamma$, small scales where $k$ is big "enough".
+The respective solutions are of the form of the damped harmonic oscillator with a shift of $-gm/k$
+\[
+x = x_0 e^{-\gamma t} e^{\pm i \sqrt{\omega_k ^2 - \gamma ^2} \, t} - \dfrac{g m}{k}
+\]
+Before recombination, the perturbations of the photon-baryon fluid behaves analogously to the damped harmonic oscillator.\\
+During matter dominated era, overdensities of dark matter creates gravitational well where the photon baryon-fluid falls in.
+As a consequence the gravitational potential compresses the baryon-photon fluid and the pressure starts to rise.
+Since dark matter and baryonic matter are pressureless, the system accretes until the photon pressure causes the fluid to expand outward.\\
+The process of compression and expansion gives rise to sound waves and it goes on until recombination.
+Only the fluctuations that are caught at the extrema of their oscillations will become peaks in the CMB power spectrum.
+Modes caught at the extrema form a harmonic series based on the distance sound can travel by recombination.
+The first peak represents the mode that compressed once inside potential wells before recombination, the second the mode that compressed and then rarefied, the third the mode that compressed then rarefied then compressed, etc.
+exactly as a spring!
+The radiation pressure acts as a spring, whereas the inertia of the fluid as the mass of the ball.\\
+The temperature fluctuations are damped due to collisions between the baryons and the photons that dissipate energy, and the expansion of the universe.\\
+%The damping scale provides another standard ruler for the curvature test
+The physical scale of the damping depends on the baryon density through the mean free path
+%And the matter density through the time available for the photons to random walk.
 
-The photon-baryon fluid is sitting in the gravitational potential wells that are the seeds of structure in the universe.
-As gravity tries to compress the fluid, radiation pressure resists resulting in acoustic oscillations.
-Because it acts to resist compression, we will represent the radiation pressure abstractly as springs.
-Likewise we will represent the inertia of the fluid, or loosely speaking its mass (really energy density), as massive balls falling under gravity:\\
-
-Modes caught at extrema of their oscillations become the peaks in the CMB power spectrum.
-They form a harmonic series based on the distance sound can travel by recombination, called the sound horizon.
-The first peak represents the mode that compressed once inside potential wells before recombination, the second the mode that compressed and then rarefied, the third the mode that compressed then rarefied then compressed, etc
-
-\subsection{Damping}
-The temperature fluctuations are damped due to collisions between the baryons and the photons that dissipate energy, and the expansion of the universe.\\
-The damping scale provides another standard ruler for the curvature test
-The physical scale of the damping depends on the baryon density through the mean free path
-And the matter density through the time available for the photons to random walk.
+\begin{comment}
 If we can calibrate the distance CMB photons random walk during recombination, we have another standard ruler for the angular diameter distance test of the spatial curvature of the universe.
@@
 Mathematically, the length is roughly the geometric mean of the mean free path and the distance light can travel without obstruction (the horizon scale).
-\begin{comment}
+%
+%
+%
+%
     This text will not be displayed.
@@
 \section{Comments on the results and plots of the CMB spectrum}
-We have seen in section 3 how general relativity and the density parameters  characterize the content of our Universe,  in section 4 the dynamics of the CMB photons is affected by matter.
-We want to link the previous theoretical results to the observations of the temperature fluctuations of the CMB sky.\\
-The temperature fluctuations are projected in the sky map and they appear to us as anisotropies in the sky map tempearature.
-
-The spherical harmonics $Y^{m} _{l} (\theta, \phi)$ compose a set of orthonormal functions on the sky.\\
-So if $T(\theta,\phi)$ is the temperature at position $(\theta,\phi)$, it is possible to decompose the temperature into a series:
+The four density parameters $\Omega$ encode the energy-matter content of the Universe and they determine the evolution of space-time through the Friedmann equations. 
+In section 4 we have outlined how we expect matter to behave at large and small scales.
+We want now to link the information contained in the fluctuations of the CMB photons to the density parameters.\\
+The behavior of the primordial plasma is imprinted in the CMB photons, in fact, we observe the density fluctuations as anisotropies in the sky map tempearature.
+In order to relate the fluctuations at different scales and the deviations from the average temperature $2.7$ K on the CMB map, it is necessary to decompose the temperature deviation $T(\theta, \phi)$ into a set of orthonormal functions on the sky.
+The spherical harmonics $Y^{m} _{l} (\theta, \phi)$ are suitable for this.\\
+So if $T(\theta,\phi)$ is the temperature at position $(\theta,\phi)$ on the sky map,
+we can write:
 \begin{equation}
@@
 \end{equation}
-Due to the orthonormality of the spherical harmonics
+Due to the orthonormality of the spherical harmonics, we obtain the coeaficients:
 \begin{equation}
 a_{lm} = \int _0 ^{2 \pi} \dd \phi \int _0  ^{\pi} \dd \theta \,
-\sin \theta \, T(\theta, \phi) \, Y^{m} _l (\theta, \phi)
+\sin( \theta) \, T(\theta, \phi) \, Y^{m} _l (\theta, \phi)
  \end{equation}
@@
  \end{equation}
+Since $l \sim 1/ \theta$, for small $l$ we are considering big scales of the sky map, viceversa for big $l$.
+As we consider increasing $l$ we are looking at fluctuations in the primordial plasma that have a decreasing  scale and thus wavelength.\\
 The measured temperature power spectrum is shown in Figure(\ref{temp_pow_spect})
@@
 %
-The Sachs-Wolfe effect is dominant on large scales, i.e. small l.\\
-The first peak is at $l \approx 200$ and the  acoustic oscillations take place.
+For large scales, small $l<30$, the power spectrum is constant and oscillations do not take place.
+Therefore, the Sachs-Wolfe effect is dominant on large scales where the oscillations have too large wavelength to complete an entire oscillations before recombination and they experience mainly the gravitational redshift.\\
+For large $l$ the acoustic oscillations are dominant.
+The first peak is at $l \approx 200$ approximately $1 ^o$ on the sky, it represents how the tiny variations in the fluid density gave rise to a sound wave which collapsed exactly at the time of recombination.
+The position of the peak tells us at which scale the first total compression of the primordial plasma happened.
+The second peak is linked to the maximal rarefaction of the plasma, so the position of the second peak tells us how the
+
 The damping effect is evident for $l>10^{3}$.\\

### 2019-02-22 paper/main.tex
section 5.2

@@
 \begin{figure}
+\centering
 \includegraphics[width=0.9\textwidth]{planck2018}
@@
 The position of the peak tells us at which scale the first total compression of the primordial plasma happened.
-The second peak is linked to the maximal rarefaction of the plasma, so the position of the second peak tells us how the
-
-The damping effect is evident for $l>10^{3}$.\\
+The second peak is linked to those oscillations that compressed and expanded, and they reached the maximal rarefaction of the plasma at recombinatio.
+The third peak is related to the oscillations that collapsed expanded and recollapsed, and so on for the higher peaks.\\
+Notice that as we consider higher and higher $l$, i.e. smaller scales, the damping effects become relevant, especially for  $l>10^{3}$.
 

### 2019-02-22 paper/main.tex
dark energy and curvature

@@
 \pagebreak
-\section{From the Discovery of the CMB to the Planck mission}
+\section{From the Discovery of the CMB to the Planck Mission}
 %
@@
 
-\section{Content of the Universe} 
+\section{Energy-Matter Content of the Universe} 
 It is often said that our Universe is made up of $68.8$\% of Dark Energy, and $26.8 $\% by Dark Matter and $4.9 $\% of ordinary matter, but what do we really mean by that?\\
@@
 \section{Comments on the results and plots of the CMB spectrum}
-The four density parameters $\Omega$ encode the energy-matter content of the Universe and they determine the evolution of space-time through the Friedmann equations. 
-In section 4 we have outlined how we expect matter to behave at large and small scales.
-We want now to link the information contained in the fluctuations of the CMB photons to the density parameters.\\
+We have outlined how we expect matter to behave at large and small scales.
+Let us now see if our predictions are compatible with the measured temperature power spectrum.
 The behavior of the primordial plasma is imprinted in the CMB photons, in fact, we observe the density fluctuations as anisotropies in the sky map tempearature.
-In order to relate the fluctuations at different scales and the deviations from the average temperature $2.7$ K on the CMB map, it is necessary to decompose the temperature deviation $T(\theta, \phi)$ into a set of orthonormal functions on the sky.
+In order to relate the fluctuations at different scales and the deviations from the average temperature $2.7$ K on the CMB map, it is necessary to decompose the observed temperature deviation $T(\theta, \phi)$ into a set of orthonormal functions on the sky.
 The spherical harmonics $Y^{m} _{l} (\theta, \phi)$ are suitable for this.\\
@@
 Since $l \sim 1/ \theta$, for small $l$ we are considering big scales of the sky map, viceversa for big $l$.
-As we consider increasing $l$ we are looking at fluctuations in the primordial plasma that have a decreasing  scale and thus wavelength.\\
-The measured temperature power spectrum is shown in Figure(\ref{temp_pow_spect})
+As we consider increasing $l$ we are looking at fluctuations in the primordial plasma that have a decreasing  scale and thus a smaller wavelength.\\
+The measured temperature power spectrum is shown in Figure(\ref{temp_pow_spect}).
 %
@@
 The third peak is related to the oscillations that collapsed expanded and recollapsed, and so on for the higher peaks.\\
-Notice that as we consider higher and higher $l$, i.e. smaller scales, the damping effects become relevant, especially for  $l>10^{3}$.
+Notice that as we consider higher and higher $l$, i.e. smaller scales, the damping effects become relevant, especially for  $l>10^{3}$.\\
+
+The four density parameters $\Omega$ encode the energy-matter content of the Universe and they determine the evolution of space-time through the Friedmann equations. 
+We want now to link the information contained in the measured fluctuations of the CMB to the density parameters through the observed power spectrum.\\
 
 \subsection{Dark Energy and Curvature}
+The cosmological constant $\Lambda$ was introduced in the Einstein's field equations as a possible parameter of our cosmological model.
+It turns out from the measurements of the Hubble constant $H_0$ and distant supernovae that the Universe is not only expanding but accelerating.
+Therefore, from the Friedmann equations we know that the cosmological constant plays a crucial role in the expansion and in the future evolution of the Universe.
+This mysterious energy that leads to the expansion of the Univers is called Dark Energy.\\
+Form Figure(\ref{DE_curv} b) we can notice that the dark energy density $\Omega_{\Lambda0}$ plays a small role in the position of the peaks. 
+In fact, the  cosmological constant produces a small change in the distance light can travel since recombination and this influences the scale at which we measure the peaks.\\
+The position of the peaks is instead particularly sensitive to the cruvature of the Universe, as show in Figure(\ref{DE_curv}a).
+The curvature determines how anlges are deformed.
+By measuring the position of the first peak we know the angle $\theta \sim 1/l$ of the oscillations.
+If I multiply by the angle by the distance (specifically the angular distance) I obtain the size of the oscillations for Euclidean geometry $k =0$.
+The first peak represents the first complete compression of the photon-bryon fluid, so by multplying the sound speed of the fluid times the time of the collapse times the expansion factor I obtain the size of the oscillations and I can compare it with the estimated size in order to check the curvature parameter.
+	TO BE EXPLAINED DECENTLY
 
-Position of peaks mainly sensitive to curvature
-Shapes fixed by the physical density of matter and baryons
-Missing or "dark energy" plays a small roll in the position of peaks
-As advertised, the position of that first peak in the power spectrum of the anisotropies, and indeed all of the peaks, depend sensitively on the spatial curvature of the universe.
-As the curvature of the universe decreases (and in fact becomes negative in the yellow curve below)\\
-the peaks move to smaller angles (higher multipole l) while preserving their shape.
-Cosmologists fraction of the critical density in matter Omegam so that as 1-Omegamincreases from zero, the universe becomes increasingly negatively curved if there is no other forms of "missing energy" that we've missed in our accounting.
-
-Caveats:
-
-In the blue curve, we assume that there is indeed a form of "missing" or dark energy in a cosmological constant that makes the universe flat despite a sub-critical density of matter.
-We see that the positions mainly care about the curvature of the universe but there is a small shift to larger angular scales (lower multipoles) through the introduction of a cosmological constant.
-This is because the cosmological constant produces a small change in the distance light can travel since recombination, a fact that is related to its well known effect on the age of the universe.
-
-Note that in the above figure we assume that the physical density of the matter (Omegamh2) is fixed.
-This is different from saying its fraction of the critical density (Omegam) is fixed since the Hubble constant (h), or expansion rate today, enters into the definition of the critical density.
-Given our current uncertainties about the physical density of the matter, the distance that sound can travel by recombination is currently uncertain, a fact related to the matter's effect on the age of the universe at recombination.
+% Given our current uncertainties about the physical density of the matter, the distance that sound can travel by recombination is currently uncertain, a fact related to the matter's effect on the age of the universe at recombination.
 Likewise we have assumed that the physical density of the baryons  (Omegabh2) is fixed.
@@
 \includegraphics[width=\textwidth]{curvature_de}
+\end{center}
 \caption{}
-
-\end{center}
 \label{DE_curv}

### 2019-02-26 paper/main.tex
dark matter discussion

@@
 \]
-Before recombination, the perturbations of the photon-baryon fluid behaves analogously to the damped harmonic oscillator.\\
+Before recombination, the perturbations of the photon-baryon fluid behaves analogously to the damped harmonic oscillator.
+The mass that elongates the spring and falls down is analogoues to the fluid falling and compressing inside a gravitational potential.\\
 During matter dominated era, overdensities of dark matter creates gravitational well where the photon baryon-fluid falls in.
@@
 The process of compression and expansion gives rise to sound waves and it goes on until recombination.
-Only the fluctuations that are caught at the extrema of their oscillations will become peaks in the CMB power spectrum.
+Only the fluctuations that are caught at the extrema of their oscillations at recombination will become peaks in the CMB power spectrum.
 Modes caught at the extrema form a harmonic series based on the distance sound can travel by recombination.
-The first peak represents the mode that compressed once inside potential wells before recombination, the second the mode that compressed and then rarefied, the third the mode that compressed then rarefied then compressed, etc.
+The first peak of the oscillations represents the mode that compressed the fluid inside potential wells before recombination only once, the second one represents the mode that compressed and then rarefied, the third one the mode that compressed then rarefied then compressed, etc.
 exactly as a spring!
-The radiation pressure acts as a spring, whereas the inertia of the fluid as the mass of the ball.\\
+The radiation pressure acts as a spring, whereas the inertia of the fluid as the mass of the ball.
+Only the compression phase is influenced by the inertia of the fluid, i.e. if the mass is heavier the displacement will be bigger $-gm/k$.
+\\
 The temperature fluctuations are damped due to collisions between the baryons and the photons that dissipate energy, and the expansion of the universe.\\
@@
 \end{equation}
-Due to the orthonormality of the spherical harmonics, we obtain the coeaficients:
+Due to the orthonormality of the spherical harmonics, we obtain the coefficients:
 \begin{equation}
@@
  \end{equation}
-Since $l \sim 1/ \theta$, for small $l$ we are considering big scales of the sky map, viceversa for big $l$.
+The decomposition in spherical harmonics allow us to study the temperature fluctuations at different scales on the sky, smaller is the scale of the fluctuations bigger is the pole $l$.
+The poles are inversely proportional to a an angle on the sky, $l \sim 1/ \theta$, for small $l$ we are considering big scales of the sky map, viceversa for big $l$.
 As we consider increasing $l$ we are looking at fluctuations in the primordial plasma that have a decreasing  scale and thus a smaller wavelength.\\
@@
 The second peak is linked to those oscillations that compressed and expanded, and they reached the maximal rarefaction of the plasma at recombinatio.
+You might think that the rarefaction should be associated with the local minimum after the first peak, but this is not the case because the power spectrum is sensitive to the absolute value of the tempereature oscillations.
 The third peak is related to the oscillations that collapsed expanded and recollapsed, and so on for the higher peaks.\\
@@
 The first peak represents the first complete compression of the photon-bryon fluid, so by multplying the sound speed of the fluid times the time of the collapse times the expansion factor I obtain the size of the oscillations and I can compare it with the estimated size in order to check the curvature parameter.
-	TO BE EXPLAINED DECENTLY
+	TO BE EXPLAINED DECENTLY\\
+	Substantially the curvature and the cosmological constant do not change the shape of the acoustic peaks but they only change shift their position on the power spectrum.
 
@@
 \end{center}
-\caption{}
+\caption{$\Omega_{tot} = 1-\Omega_{k0}$}
 \label{DE_curv}
@@
 \subsection{Dark Matter and Baryons}
-Baryons (or ordinary matter) load down the photon-baryon plasma and add inertial (and gravitational) mass to the oscillating system.
-
-Their effect on the acoustic peaks is easy to understand.
-Remember what happens when you add mass to a spring and let it fall in the gravitational field of the Earth.
+The matter density parameter $\Omega_{m0}$ includes any form of non-relativistic matter that interacts gravitationally, so it includes both dark matter and baryonic matter.
+Baryonic matter couples to radiation through the electromagnetic intereaction and it adds inertial mass to the oscillating photon-baryon fluid.
+What happens when you add mass to a spring and let it fall in the gravitational field of the Earth.  
 With more mass loading the spring, it falls further before pulled back by the spring. 
 On the other hand, it rebounds to the same position it started from. 
+Since odd numbered acoustic peaks are associated with how much the plasma compresses, they are enhanced by an increase in the amount of baryons.
+The even numbered peaks (second, fourth, sixth) are associated with how far the plasma "rebounds" (how much the plasma rarefies).
+Therefore, it is possible to measure the baryon content by studying the relative height of the first peak with respect to the second one.
+More baryons would enhance the odd peaks and suppress the even ones as shown in Figure(\ref{DM_bary}a).\\
+Increasing the mass of the spring would decrease the oscillations of the spring $\omega_k = \sqrt{k/m}$.
+By keeping the frequency of the oscillations constant as we increase the mass we have to increase $k$.
+Therefore the oscillations will occur at smaller scales $\lambda =2 \pi /k$ and the position of the peaks is pushed to slightly higher multipoles $l$ (Figure(\ref{DM_bary})).\\
+In addition baryons influence also damping effects.\\
+Radiation pressure plays the role of the spring and it is the only relevant pressure that makes expand the fluid.
+As the matter density parameter $\Omega_{m0}$ decreases the acoustic peaks are enhanced, because the pressure easily fights against gravity and it causes the fluid to expand outward.
+Decreasing the matter density also affects the baryon loading since the dark matter potential wells go away leaving nothing for the baryons to fall into.
+By eliminating gravitational potentials, photon-baryon acous- tic oscillations eliminate the alternating peak heights from baryon loading \cite{CMB dodelson Hu} as it is evident from Figure(\ref{DM_bary}b).\\
+On the other hand, raising the dark matter density reduces the overall amplitude of the peaks.
 
-Since the odd numbered (first, third, fifth...) acoustic peaks are associated with how far the plasma "falls" into gravitational potential wells (how much the plasma compresses), they are enhanced by an increase in the amount of baryons in the universe.
-The even numbered peaks (second, fourth, sixth) are associated with how far the plasma "rebounds" (how much the plasma rarefies).
-Thus with the addition of baryons the odd peaks are enhanced over the even peaks.
-For example, baryons make the first acoustic peak much larger than the second.
-The more baryons the more the second peak is relatively suppressed.
+The third peak is linked to a cycle of compression rarefaction and again compression of the fluid.
+Higher is the dark matter density, stronger will be the potential well which compresses the fluid.
+Therefore, an high third peak (with respect to the first peak) is an indication of dark matter.
+%Having a third peak that is boosted to a height comparable to or exceeding the second peak is an indication that dark matter dominated the matter density in the plasma before recombination.
+
 \par
 
+%There are two other related effects due to the baryons:  since adding mass to a spring slows the oscillation down, adding baryons to the plasma decrease the frequency of the oscillations pushing the position of the peaks to slightly higher multipoles l.
+%Dark matter, instead, interacts only gravitationally and it produces the gravitational wells where the plasma falls into.\\
+
 %http://background.uchicago.edu/~whu/intermediate/baryons2.html
-\paragraph{image}
-Power spectrum shows baryons enhance every other peak.
-Second peak is suppressed compared with the first and third
-Additional effects on the peak position and damping yield consistency checks
-When we do the full calculation of the power spectrum, the basic physics of a mass on the spring appears as advertised.
-The odd numbered acoustic peaks in the power spectrum are enhanced in amplitude over the even numbered ones as we increase the baryon density of the universe.\\
-Note: Cosmologists label the baryon density in terms of its fraction of the critical density Wbtimes the Hubble constant squared (in units of 100 km/s/Mpc) to get something proportional to the physical density of the baryons.]
 
-There are two other related effects due to the baryons:  since adding mass to a spring slows the oscillation down, adding baryons to the plasma decrease the frequency of the oscillations pushing the position of the peaks to slightly higher multipoles l.
+%Baryons also affect the way the sound waves damp and hence how the power spectrum falls off at high multipole moment lor small angular scales as we will see later.
 
-Baryons also affect the way the sound waves damp and hence how the power spectrum falls off at high multipole moment lor small angular scales as we will see later.
+%Note that the self-gravity of the photons and baryons still plays a role in the first and second peaks so that the third peak is the cleanest test of this behavior.
 
-The many ways that baryons show up in the power spectrum imply that the power spectrum has many independent checks on the baryon density of the universe.
-The baryon density is a quantity that the CMB can measure to exquisite precision.
-
-\paragraph{dark matter}
-Second peak is observed to be substantially lower than first peak
-Dark baryons of at least the big-bang nucleosynethesis density required
-Although we cannot yet claim that the second peak is as precisely measured as the first, we can say that (assuming it exists!) it is definitely of lower amplitude than the first:\\
-The current data indicate that the baryon density is around Omegabh2=0.02 This value is interesting since it is also the baryon density inferred from the abundance of deuterium at high redshift in quasar absorption lines and the theory of big-bang nucleosynthesis.
-We now have an additional and independent line of evidence that there are missing baryons in the universe - i.e.
-that most the baryons are not in stars.
-Once the second and higher peaks are definitively measured, CMB constraints on the baryon density will sharpen considerably (ultimately to a few percent accuracy).
-Needless to say it will be interesting to see how these comparisons shape up as the data improve.
-\paragraph{dark}
-Raising the dark matter density reduces the overall amplitude of the peaks.
-Lowering the dark matter density eliminates the baryon loading effect so that a high third peak is an indication of dark matter.
-With three peaks, its effects are distinct from the baryons
-Measuring the dark matter density resolves the main ambiguity in the curvature measurement
-As advertised the acoustic peaks in the power spectrum are sensitive to the dark matter density in the universe.
-(Formally, the matter to radiation ratio but the radiation density is fixed in the standard model.)\\
-As we raise the physical density of the dark matter, Wmh2, the driving effect goes away at a given peak such that its amplitude decreases.
-Although this effect changes the heights of all the peaks, it is only separable from the baryonic effects with at least three peaks.
-Note that decreasing the matter density also affects the baryon loading since the dark matter potential wells go away leaving nothing for the baryons to fall into.
-Having a third peak that is boosted to a height comparable to or exceeding the second peak is an indication that dark matter dominated the matter density in the plasma before recombination.
-Note that the self-gravity of the photons and baryons still plays a role in the first and second peaks so that the third peak is the cleanest test of this behavior.
-
-Notice also that the location of the peaks, and that of the first peak in particular, changes as we change the dark matter density.
+%Notice also that the location of the peaks, and that of the first peak in particular, changes as we change the dark matter density.
 The matter to radiation ratio also controls the age of the universe at recombination and hence how far sound can travel relative to how far light travels after recombination.
@@
 \includegraphics[width=\textwidth]{baryon_m}
+\end{center}
 \caption{aa}
-\end{center}
-\label{DM_bar}
+\label{DM_bary}
 \end{figure}
+
 \section{Conclusion}
-nn
-\citep{padmanabhanDetectingDarkMatter2005}
+The many ways that baryons show up in the power spectrum imply that the power spectrum has many independent checks on the baryon density of the universe.
+The baryon density is a quantity that the CMB can measure to exquisite precision.
 

### 2019-02-27 paper/main.tex
first draft

@@
 \end{equation}
-Solving the full general-relativistic description of the photon-matter fluid requires a long and complicated treatment [BAUMANN], so we use instead an analogy with the most favourite model of a physicist: the harmonic oscillator\footnote{As in every analogy in physics, the phenomena are not the same.
+Solving the full general-relativistic description of the photon-matter fluid requires a long and complicated treatment \cite{LecturesPdf}, so we use instead an analogy with the most favourite model of a physicist: the harmonic oscillator\footnote{As in every analogy in physics, the phenomena are not the same.
 A mass on a spring is not the same as a relativistic fluid perturbation in an expanding 4-dimensional manifold, but the analogy is very helpful for the understanding and the equations are not that different (in first approximation)}.\\
@@
 By measuring the position of the first peak we know the angle $\theta \sim 1/l$ of the oscillations.
-If I multiply by the angle by the distance (specifically the angular distance) I obtain the size of the oscillations for Euclidean geometry $k =0$.
-The first peak represents the first complete compression of the photon-bryon fluid, so by multplying the sound speed of the fluid times the time of the collapse times the expansion factor I obtain the size of the oscillations and I can compare it with the estimated size in order to check the curvature parameter.
+By multiplying this angle and the angular distance (specifically the angular distance) we obtain the size of the oscillations for Euclidean geometry $k =0$.
+Since the first peak represents the first complete compression of the photon-bryon fluid, we can compare the size of the oscillations obtained with $k=0$ with the value obtained by multplying the sound speed of the fluid times the time of the collapse times the expansion factor.\\
 TO BE EXPLAINED DECENTLY\\
@@
 Decreasing the matter density also affects the baryon loading since the dark matter potential wells go away leaving nothing for the baryons to fall into.
-By eliminating gravitational potentials, photon-baryon acous- tic oscillations eliminate the alternating peak heights from baryon loading \cite{CMB dodelson Hu} as it is evident from Figure(\ref{DM_bary}b).\\
+By eliminating gravitational potentials, photon-baryon acous- tic oscillations eliminate the alternating peak heights from baryon loading \cite{huCosmicMicrowaveBackground2001} as it is evident from Figure(\ref{DM_bary}b).\\
 On the other hand, raising the dark matter density reduces the overall amplitude of the peaks.
@@
 Therefore, an high third peak (with respect to the first peak) is an indication of dark matter.
-%Having a third peak that is boosted to a height comparable to or exceeding the second peak is an indication that dark matter dominated the matter density in the plasma before recombination.
+In addition, having a third peak that is boosted to a height comparable to or exceeding the second peak is an indication that dark matter dominated the matter density in the plasma before recombination .
 
@@
 
-%http://background.uchicago.edu/~whu/intermediate/baryons2.html
+%
 
@@
 
+\nocite{*}
+
 \bibliographystyle{plain}

### 2019-02-27 paper/main.tex
corrections

@@
 As the number density of the free electrons dropped with the expansion, the Thomson scattering $e^- + \gamma  \rightarrow e^- + \gamma$ became inefficient and the photons have since streamed freely through the universe in all directions and they are today observed as the Cosmic Microwave Background \citep{LecturesPdf}.\\
-The Cosmic Microwave Background appears to us as the best measured Planck spectrum that we know with fluctuations of order $10 ^{-5}$ around the average temperature $T_{CMB} =2.725$ K.
+The Cosmic Microwave Background appears to us as the best measured Planck spectrum that we know with fluctuations of order $10 ^{-5}$ around the average temperature $T_{CMB} =2.7$ K.
 The fluctuations are extremely important because they contain the crucial information about the primordial plasma and its content. 
 In fact, during the early stages of the Universe, the photons were interacting with baryonic matter, which in turn was interacting gravitationally with dark matter.
-Thus, the observations of the CMB fluctuations are linked to the energy-matter content of our Universe and dark matter.\\
-The aim of this paper is to give a short and concise overview of the physics of the CMB and the cosmological evidence of Dark Matter through the analysis of the CMB fluctuations within the $\Lambda$CDM model assumptions.
-We are interested in providing few but fundamental tools to understand the importance of the CMB for Dark Matter.\\
+Thus, the observations of the CMB fluctuations are linked to the energy-matter content of our Universe and to dark matter.\\
+The aim of this paper is to give a short and concise overview of the physics of the CMB and the cosmological evidence of Dark Matter through the analysis of the CMB fluctuations within the $\Lambda$CDM model assumptions.\\
 We first give an historical overview of the discovery and measurements of the CMB, then we discuss the main assumptions of the $\Lambda$CDM model and the link between the content of our universe and the cosmological model.
-Afterwards, the phenomenology of the hot plasma is explained with a simplified treatment in order to understand the power spectrum of the CMB.
+Then, the physics of the hot plasma is explained with a simplified treatment in order to explain the main features of the power spectrum of the CMB.
 We conclude with the discussion of the CMB temperature power spectrum and the role of dark matter.
@@
 The discovery of the CMB created a big excitement and a new era of cosmology began.
-Measuring the CMB spectrum and its deviation from the black body spectrum was the new challange.
+Measuring the CMB spectrum and its deviation from the black body spectrum was the new challenge.
 \\
@@
 This problem could be overcomed by observing the CMB in different bands and from locations where the atmospheric humidity is low, at high altitudes and at low temperatures.
-However, the best way to meseaure the CMB spectrum is to use satellites.\\
-The first sattellite that was launched to observe the CMB was COBE. 
+However, the best way to measure the CMB spectrum is to use satellites.\\
+The first satellite that was launched to observe the CMB was COBE. 
 It did provide a convincing first detection of the CMB anisotropy, and it played a crucial role in determining the viability of the different cosmological models at that time.
@@
 \caption{The microwave sky as seen by the COBE DMR (differential microwave radiometer) instrument.
-The top panel shows the microwave sky as seen on a linear tem- perature scale including zero.
+The top panel shows the microwave sky as seen on a linear temperature scale including zero.
 No anisotropies are visible in this image, because the CMB monopole at 2.725K dominates.
 In the middle panel, the monopole component has been subtracted.
-Apart from some slight contamination from the galaxy near the equator (corre- sponding to the plane of our Galaxy), one sees only a nearly perfect dipole pattern, owing to our peculiar motion with respect to the rest frame defined by the CMB.
+Apart from some slight contamination from the galaxy near the equator (corresponding to the plane of our Galaxy), one sees only a nearly perfect dipole pattern, owing to our peculiar motion with respect to the rest frame defined by the CMB.
 In the bottom panel, both the monopole and dipole components have been removed.
@@
 We assume that the observable properties of the Universe are isotropic and there is not a preferred direction. 
-Therefore, the Universe is assumed to be homogenous and isotropic at enough large scales $> 100$ Mpc, at least up to the observable universe.\\
+Therefore, the Universe is assumed to be homogeneous and isotropic at enough large scales $> 100$ Mpc, at least up to the observable universe.\\
 Another important assumption is that there exists a class of observers at rest with respect to the Cosmic Microwave Background \citep{bartelmannStandardModelCosmology}.
@@
 The scale factor $a(t)$ determines how the distances scale with the evolution of the Universe.
-The propagation condition of light is $ds^2 =0$, which implies that the light with frequency $\nu$ and the wavelength $\lambda$ is red- or blueshifted by the same amount as space expands or shrinks:
+The propagation condition of light is $ds^2 =0$, which implies that the light with frequency $\nu$ and the wavelength $\lambda$ is red- or blue-shifted by the same amount as space expands or shrinks:
 \begin{equation}
@@
 \\
-Notice that the FLRW metric has $g_{0 i}=0$ due to the isotropy and the two parameters $a(t)$ and $k$ are the only allowed to preserve our assumptions, all the others parameter that we can introduce can be absorbed in these two.
+Notice that the FLRW metric has $g_{0 i}=0$ due to the isotropic assumption and the two parameters $a(t)$ and $k$ are the only allowed to preserve our assumptions, all the others parameter that we can introduce can be absorbed in these two.
 \\ % comments on the redshift, metric, what spatially flat means
-If we assume the correctnes of the General Theory of Relativity, we can use the Einstein's field equations
+If we assume the correctness of the General Theory of Relativity, we can use the Einstein's field equations
 \begin{equation}
@@
 the number of particles per unit volume decreases with the expansion.
-The energy density of radiation $u = \rho_r c^2 $ decreases with the power of four because photons experience not only the dilution due to the spatial expansion but their frequencies, accordingly their energies, decreased by the streching of spacetime.\\
+The energy density of radiation $u = \rho_r c^2 $ decreases with the power of four because photons experience not only the dilution due to the spatial expansion but their frequencies, accordingly their energies, decreased by the stretching of spacetime.\\
 We now rewrite the first Friedmann equation as
@@
 In the other limit the future of the Universe is determined by the cosmological constant $\Lambda$.
-We have not specified the nature of the cosmological constant, up to now it has been trated as a possible parameter that can be added to the Einstein's field equations(\ref{einstein_eq}).
+We have not specified the nature of the cosmological constant, up to now it has been treated as a possible parameter that can be added to the Einstein's field equations(\ref{einstein_eq}).
 \\
@@
 The fluctuations of the primordial fluid can be characterized by a typical scale $\lambda = 2 \pi /k$ of oscillation/propagation that could depends on the local gravitational pull, pressure or other properties.
-It is important to stress that $k$ is not a wavevector, but it acts as it was. 
+It is important to stress that $k$ is not a wavevector, but it behaves as it was. 
 In fact, the $k$ parameter will represent the strength of the spring.
 If $k$ is small, the spring is loose and it  oscillates over large scales $\lambda$, analogously the oscillations of the fluctuations will have a large wavelength. \\ 
-In addition, fluctuations are damped due to the expasion of the Universe and due to collisions, and ultimately they feel a constant gravitational pull from the overall fluid.
+In addition, fluctuations are damped due to the expansion of the Universe and due to collisions, and ultimately they feel a constant gravitational pull from the overall fluid.
 By analogy with the mass-spring system we analyze the fluctuations at different scales by solving the well known equation:
@@
 In the photon-baryon fluid, perturbation modes of very large scales (large $\lambda$, very small $k$) do not have the time to complete an entire oscillation before recombination and they are influenced only by the gravitational potential of the overdensities.
-As a consequence of the Einstein's equivalence principle, photons that escape from a gravitational field are redshifted.
-If we consider the fluctuations of the CMB on large scales, the photons that tries to escape from the gravitational well created by matter are redshifted according to the so-called Sachs-Wolfe effect.
+As a consequence of the Einstein's equivalence principle, photons that escape from a gravitational field are red-shifted.
+If we consider the fluctuations of the CMB on large scales, the photons that tries to escape from the gravitational well created by matter are red-shifted according to the so-called Sachs-Wolfe effect.
 The theoretical result from the relativistic derivation gives a temperature fluctuation $\Theta = -\delta \Phi /(3c^2)$.
@@
 Before recombination, the perturbations of the photon-baryon fluid behaves analogously to the damped harmonic oscillator.
-The mass that elongates the spring and falls down is analogoues to the fluid falling and compressing inside a gravitational potential.\\
+The mass that elongates the spring and falls down is analogues to the fluid falling and compressing inside a gravitational potential.\\
 During matter dominated era, overdensities of dark matter creates gravitational well where the photon baryon-fluid falls in.
@@
 The decomposition in spherical harmonics allow us to study the temperature fluctuations at different scales on the sky, smaller is the scale of the fluctuations bigger is the pole $l$.
-The poles are inversely proportional to a an angle on the sky, $l \sim 1/ \theta$, for small $l$ we are considering big scales of the sky map, viceversa for big $l$.
+The poles are inversely proportional to a an angle on the sky, $l \sim 1/ \theta$, for small $l$ we are considering big scales of the sky map, vice versa for big $l$.
 As we consider increasing $l$ we are looking at fluctuations in the primordial plasma that have a decreasing  scale and thus a smaller wavelength.\\
@@
 The position of the peak tells us at which scale the first total compression of the primordial plasma happened.
-The second peak is linked to those oscillations that compressed and expanded, and they reached the maximal rarefaction of the plasma at recombinatio.
-You might think that the rarefaction should be associated with the local minimum after the first peak, but this is not the case because the power spectrum is sensitive to the absolute value of the tempereature oscillations.
-The third peak is related to the oscillations that collapsed expanded and recollapsed, and so on for the higher peaks.\\
+The second peak is linked to those oscillations that compressed and expanded, and they reached the maximal rarefaction of the plasma at recombination.
+You might think that the rarefaction should be associated with the local minimum after the first peak, but this is not the case because the power spectrum is sensitive to the absolute value of the temperature oscillations.
+The third peak is related to the oscillations that collapsed expanded and re-collapsed, and so on for the higher peaks.\\
 Notice that as we consider higher and higher $l$, i.e. smaller scales, the damping effects become relevant, especially for  $l>10^{3}$.\\
@@
 In fact, the  cosmological constant produces a small change in the distance light can travel since recombination and this influences the scale at which we measure the peaks.\\
-The position of the peaks is instead particularly sensitive to the cruvature of the Universe, as show in Figure(\ref{DE_curv}a).
-The curvature determines how anlges are deformed.
+The position of the peaks is instead particularly sensitive to the curvature of the Universe, as show in Figure(\ref{DE_curv}a).
+The curvature determines how angles are deformed.
 By measuring the position of the first peak we know the angle $\theta \sim 1/l$ of the oscillations.
 By multiplying this angle and the angular distance (specifically the angular distance) we obtain the size of the oscillations for Euclidean geometry $k =0$.
-Since the first peak represents the first complete compression of the photon-bryon fluid, we can compare the size of the oscillations obtained with $k=0$ with the value obtained by multplying the sound speed of the fluid times the time of the collapse times the expansion factor.\\
+Since the first peak represents the first complete compression of the photon-baryon fluid, we can compare the size of the oscillations obtained with $k=0$ with the value obtained by multiplying the sound speed of the fluid times the time of the collapse times the expansion factor.\\
 TO BE EXPLAINED DECENTLY\\
@@
 The matter density parameter $\Omega_{m0}$ includes any form of non-relativistic matter that interacts gravitationally, so it includes both dark matter and baryonic matter.
-Baryonic matter couples to radiation through the electromagnetic intereaction and it adds inertial mass to the oscillating photon-baryon fluid.
+Baryonic matter couples to radiation through the electromagnetic interaction and it adds inertial mass to the oscillating photon-baryon fluid.
 What happens when you add mass to a spring and let it fall in the gravitational field of the Earth.  
@@
 Decreasing the matter density also affects the baryon loading since the dark matter potential wells go away leaving nothing for the baryons to fall into.
-By eliminating gravitational potentials, photon-baryon acous- tic oscillations eliminate the alternating peak heights from baryon loading \cite{huCosmicMicrowaveBackground2001} as it is evident from Figure(\ref{DM_bary}b).\\
+By eliminating gravitational potentials, photon-baryon acoustic oscillations eliminate the alternating peak heights from baryon loading \cite{huCosmicMicrowaveBackground2001} as it is evident from Figure(\ref{DM_bary}b).\\
 On the other hand, raising the dark matter density reduces the overall amplitude of the peaks.

### 2019-02-27 paper/main.tex
almost done

@@
 \tensordelimiter{:}
+\usepackage{stackengine}
 
@@
 The aim of this paper is to give a short and concise overview of the physics of the CMB and the cosmological evidence of Dark Matter through the analysis of the CMB fluctuations within the $\Lambda$CDM model assumptions.\\
-We first give an historical overview of the discovery and measurements of the CMB, then we discuss the main assumptions of the $\Lambda$CDM model and the link between the content of our universe and the cosmological model.
-Then, the physics of the hot plasma is explained with a simplified treatment in order to explain the main features of the power spectrum of the CMB.
-We conclude with the discussion of the CMB temperature power spectrum and the role of dark matter.
+We first give an historical overview of the discovery and measurements of the CMB, then we discuss the main assumptions of the $\Lambda$CDM model and the link between the energy-matter content of the Universe and the cosmological model.
+Afterwards, the physics of the primordial plasma is explained through an analogy with a spring-mass system.
+In section 5 we explain how the phenomena in the primordial plasma are reflected in the measured temperature power spectrum of the CMB.
+Lastly, we discuss how the different energy-matter components influence the CMB power spectrum and we conclude that dark matter is one of the leading constituents of the universe.
 
@@
 %
-In the 1960s Penzias and Wilson measured an isotropic and constant with time strong signal coming from the sky by using a horn-reflector radio antenna (Figure(\ref{antenna})). 
+In the 1960s Penzias and Wilson measured an isotropic and constant with time strong signal coming from the sky by using a horn-reflector radio antenna shown in Figure(\ref{antenna}). 
 They tried everything they could do to reduce the “noise” in their system, but the signal remained.\\
-In 1965 Arno Penzias and Robert Wilson published the paper: \emph{A measurement of excess antenna temperature at
+In 1965 Penzias and Wilson published the paper: \emph{A measurement of excess antenna temperature at
 4080 Mc/s}, where they reported the measurements of an isotropic, unpolarized, and free from seasonal variations excess noise temperature
 \citep{penziasMeasurementExcessAntenna1965}.
-The explanation of that signal was given by Robert Dicke and his research group at Princeton University: such signal as the relic of an early, hot, dense, and opaque state of the universe\footnote{The existence of the cosmic background radiation had actually been predicted by the physicist George Gamow and his colleagues in 1948} \citep{bucherPhysicsCosmicMicrowave2015}
+The explanation of that signal was given by Robert Dicke and his research group at Princeton University: Penzias and Wilson discovered the relic of an early, hot, dense, and opaque state of the universe\footnote{The existence of the cosmic background radiation had actually been predicted by the physicist George Gamow and his colleagues in 1948} \citep{bucherPhysicsCosmicMicrowave2015}
 . \\
@@
 In fact, microwaves with wavelengths shorter than $\lambda \sim 3$ cm are strongly absorbed by water molecules \citep{RydenIntroCosmoPdf}.
-This problem could be overcomed by observing the CMB in different bands and from locations where the atmospheric humidity is low, at high altitudes and at low temperatures.
-However, the best way to measure the CMB spectrum is to use satellites.\\
-The first satellite that was launched to observe the CMB was COBE. 
+This problem could be overcome by observing the CMB in different bands and from locations where the atmospheric humidity is low, at high altitudes and at low temperatures.
+However, any terrestrial experiment would be able to measure only a portion of the sky map and would be affected by Earth's atmosphere, so the best way to measure the CMB spectrum is to use satellites.\\
+COBE was the first satellite launched to measure the CMB in 1989. 
 It did provide a convincing first detection of the CMB anisotropy, and it played a crucial role in determining the viability of the different cosmological models at that time.
 \\
-After that, WMAP and PLanck space missions  increased the accuracy of the measurements Figure (\ref{cobe_wmap_planck}).\\
-The COBE, WMAP and Planck missions measured the CMB anisotropies with increasing accuracy.
-COBE, the first CMB satellite, measured fluctuations to scales of 7$^\circ$.
-WMAP was able to measure resolutions down to 0.3$^\circ$ in five different frequency bands, with Planck measuring all the way down to just 5 arcminutes (0.07$^\circ$) in nine different frequency bands in total.\\
+After COBE, WMAP and Planck satellites measured the CMB anisotropies with increasing accuracy  Figure (\ref{cobe_wmap_planck}).\\
+COBE measured fluctuations to scales of 7$^\circ$, WMAP was able to measure resolutions down to 0.3$^\circ$ in five different frequency bands, and Planck measured all the way down to just 5 arcminutes (0.07$^\circ$) in nine different frequency bands in total.\\
 Nevertheless the satellites improved their accuracy, many other sources of noise were encountered such as the light coming from the center of our galaxy, other stars and other objects in the universe, in addition to the relative motion of the satellite with respect to the CMB (Figure (\ref{cobe_map})).\\
 Finally, observations and statistical analysis showed that the CMB spectrum is close to a black body spectrum up to fluctuations of order of $10^{-5}$ K (Figure (\ref{cobe_blackbody})).\\
+The technological efforts for precisely measuring the fluctuations of the CMB was a fundamental step-stone to understand what the universe is made of.
 % maybe last sentence in the introduction with the image
@@
    {\includegraphics[height=7cm]{blackbody}}
-\caption{}
+\caption{The monopole spectrum of the Cosmic Microwave Background Radiation using the original data set by the FIRAS team, available at \url{http://lambda.gsfc.nasa.gov/product/cobe/firas_monopole_get.cfm}.
+The vertical axis "MJy/sr" corresponds to $10^6$ jansky per steradian, where a jansky is $10^{-26}$ Watts per square-meter per Hertz.
+The horizontal axis ("1/cm") corresponds to the reciprocal of the microwave wavelength (in cm), which is proportional to the microwave frequency.
+The error bars are too small to be displayed by a computer screen, but vastly exaggerated error bars were included to show the measured data points.}
 \label{cobe_blackbody}
@@
 In the bottom panel, both the monopole and dipole components have been removed.
-Except for the galactic contamination around the equator, one sees the cosmic microwave background anisotropy along with some noise.
+Except for the galactic contamination around the equator, one sees the CMB anisotropy along with some noise \cite{bucherPhysicsCosmicMicrowave2015}.
 (Credit: NASA/COBE Science Team)}
@@
 \section{Energy-Matter Content of the Universe} 
-It is often said that our Universe is made up of $68.8$\% of Dark Energy, and $26.8 $\% by Dark Matter and $4.9 $\% of ordinary matter, but what do we really mean by that?\\
-In this section we explain the meaning of these parameters and what is Universe made up of. 
-The assumptions and the theoretical framework that we are going to explain will be then used to analyze the observations of the CMB.\\
+It is often said that the Universe we live in is flat and it is made up of $69$\% of Dark Energy, and $26 $\% by Dark Matter and $5$\% of ordinary matter, but what do we really mean by that?\\
+In this section we explain the meaning of these parameters and from which theoretical framework they come from. 
+We are going to use the assumptions of the so-called $\Lambda$CDM model.\\
 We assume that the observable properties of the Universe are isotropic and there is not a preferred direction. 
 Therefore, the Universe is assumed to be homogeneous and isotropic at enough large scales $> 100$ Mpc, at least up to the observable universe.\\
-Another important assumption is that there exists a class of observers at rest with respect to the Cosmic Microwave Background \citep{bartelmannStandardModelCosmology}.
+Another important assumption is that there exists a class of observers at rest with respect to the Cosmic Microwave Background such that the previous assumptions are valid \citep{bartelmannStandardModelCosmology}.
 Let us clarify this concept.
@@
 After subtracting the average temperature of the CMB from its spectrum, a moving observer with respect with the CMB will see a dipole pattern, where the blue-shifted photons come from the direction the observer is moving toward to and the red-shifted photons from the opposite direction.
-Since Earth is not at rest with respect to the CMB, the satellite COBE measured the dipole pattern showed in the second panel in Figure (\ref{cobe_map}).\\
-In addition we assume that space-time is described by a metric theory of gravity, and we treat space-time as a 4-dimensional manifold characterized by the metric tensor $g_{\mu \nu}$.
+Since Earth is not at rest with respect to the CMB, the satellite COBE measured the dipole pattern showed in the second panel in Figure (\ref{cobe_map}).
+And therefore from an observer on Earth the Universe is not isotropic.
+In the following sections we consider only those observers which are at rest with respect to the Cosmic Microwave Background.\\
+In addition we assume that spacetime is described by a metric theory of gravity, and we treat spacetime as a 4-dimensional manifold characterized by the metric tensor $g_{\mu \nu}$.
 The most general metric $g_{\mu \nu}$ satisfying homogeneity and isotropy assumptions is the Friedmann – Lemaître – Robertson – Walker (FLRW) metric written here in terms of the invariant geodesic distance $\dd s ^2 = g_{\mu \nu} \dd x^{\mu} \dd x^{\nu}$:
@@
 \end{equation}
-where $k$ is the space curvature and it determines the geometry of the spatial dimensions, elliptical, Euclidean or hyperbolic for $k>0$, $k=0$ or $k<0$.
+By defining $g_{\mu \nu}$ we are basically  defining how time and space intervals are measured.
+Spacetime is treated as a manifold because it shares the property with manifolds to be locally flat\footnote{locally flat means  that locally it appears as the Minkowski spacetime}.\\
+$k$ is the space curvature and it determines the geometry of the spatial dimensions, elliptical, Euclidean or hyperbolic for $k>0$, $k=0$ or $k<0$.
 The space curvature determines in which kind of three dimensional space we live in and how angles are measured.\\
@@
 where $\rho$ and $p$ are, respectively, the mass density and the pressure of the fluid.\\
-Solving (\ref{einstein_eq})and using the above definition (\ref{energy-momentum-tensor}) (which is a rather long and tedious derivation), gives us the Friedmann equation:
+Solving (\ref{einstein_eq}) and using the above definition (\ref{energy-momentum-tensor}) (which is a rather long and tedious derivation), gives us the Friedmann equations:
 \begin{equation}
@@
 where  $\dot{}$  represents the time derivative.\\
-The first Friedmann equation tells us how the Hubble parameter$H(t)$, i.e. the expansion rate,  evolves according to what is contained in our Universe.
+The first Friedmann equation tells us how the Hubble parameter $H(t)$, i.e. the expansion rate,  evolves according to what is contained in our Universe.
 The second Friedmann equation tells how the Universe accelerates.\\
@@
  \end{comment}
-Solving this for dust (a name for non-relativistic matter) $\rho_m c^2 << p_m$ and for radiation $\rho_r c^2 = p_r/3$ gives
+Solving this for dust, i.e. non-relativistic matter, $\rho_m c^2 << p_m$ and for radiation $\rho_r c^2 = p_r/3$ gives
 \begin{equation}
@@
 the number of particles per unit volume decreases with the expansion.
-The energy density of radiation $u = \rho_r c^2 $ decreases with the power of four because photons experience not only the dilution due to the spatial expansion but their frequencies, accordingly their energies, decreased by the stretching of spacetime.\\
+The energy density of radiation $u = \rho_r c^2 $ decreases with the power of four because photons experience not only the dilution due to the spatial expansion but their frequencies, accordingly their energies, decrease by the stretching of spacetime.\\
 We now rewrite the first Friedmann equation as
@@
 So the experimental measurements of these parameters must add up to one.
-We will see in the next sections how the CMB power spectrum puts constraints on these parameters and tell use that there is a form of matter that we cannot wee.
+We will see in the next sections how the CMB power spectrum puts constraints on these parameters and tell us that there is a form of matter that we cannot see in $\Omega_{m0}$.
 
@@
 The Cosmic Microwave Background fluctuations were produced when radiation and matter were interacting in the early stage of the Universe.
-Before the release of the CMB at $z > 1100$ the electromagnetic radiation is firmly coupled (both energetically and kinetically) to the baryons.
-The behavior of such a system can be solved by using the equations of relativistic hydrodynamics and the Einstein's field equations (\ref{einstein_eq}) with small perturbations of density $\delta \rho$, pressure $\delta p$ and gravitational potential  $\delta \Phi$.
+Before the release of the CMB at redshift $z > 1100$ the electromagnetic radiation is firmly coupled (both energetically and kinetically) to the baryons.
+The behavior of such a system can be studied by solving the equations of relativistic hydrodynamics and the Einstein's field equations (\ref{einstein_eq}) with small perturbations of density $\delta \rho$, pressure $\delta p$ and gravitational potential  $\delta \Phi$.
 Perturbations of different scales propagate as sound waves through the plasma until they are frozen at the time of recombination and they appear to us as temperature fluctuations $\Theta = \delta T /T$ in the CMB map.
@@
 \end{equation}
-Solving the full general-relativistic description of the photon-matter fluid requires a long and complicated treatment \cite{LecturesPdf}, so we use instead an analogy with the most favourite model of a physicist: the harmonic oscillator\footnote{As in every analogy in physics, the phenomena are not the same.
+Solving the full general-relativistic description of the photon-matter fluid requires a long and complicated treatment that can be found here \cite{LecturesPdf,keskitaloEffectMatterBaryon}.
+We use instead an analogy with the most favourite model of a physicist: the harmonic oscillator\footnote{As in every analogy in physics, the phenomena are not the same.
 A mass on a spring is not the same as a relativistic fluid perturbation in an expanding 4-dimensional manifold, but the analogy is very helpful for the understanding and the equations are not that different (in first approximation)}.\\
@@
 \end{equation}
-We will discuss the overall behavior of the photon-baryon fluid at different scales $\lambda$ by studying the solutions of the harmonic oscillator for different $k$.
+We will discuss the overall behavior of the photon-baryon fluid fluctuations with different scales $\lambda$ by studying the solutions of the damped harmonic oscillator for different $k$.
 
@@
 In the photon-baryon fluid, perturbation modes of very large scales (large $\lambda$, very small $k$) do not have the time to complete an entire oscillation before recombination and they are influenced only by the gravitational potential of the overdensities.
-As a consequence of the Einstein's equivalence principle, photons that escape from a gravitational field are red-shifted.
-If we consider the fluctuations of the CMB on large scales, the photons that tries to escape from the gravitational well created by matter are red-shifted according to the so-called Sachs-Wolfe effect.
-The theoretical result from the relativistic derivation gives a temperature fluctuation $\Theta = -\delta \Phi /(3c^2)$.
-The Sachse Wolfe effect takes into account an additional effect that cannot be explained with the simple harmonic oscillator model and it arises from the time dilation due to the expansion of the Universe.
+As a consequence of the Einstein's equivalence principle, photons that escape from a gravitational field are red-shifted, photons that fall into a gravitational field are blue-shifted.
+Photons associated with fluctuations with large $\lambda$ try to escape from the gravitational well created by matter at the time of recombination and, therefore, they are red-shifted.
+A photon which happens to be at a potential maximum when the universe became transparent gains energy as it falls down the “potential hill”, and thus is blue-shifted.
+A detailed general relativistic calculation gives a temperature fluctuation $\Theta = -\delta \Phi /(3c^2)$.
+This is called the Sachs-Wolfe effect.
+The Sachs-Wolfe effect takes into account an additional effect that cannot be explained with the simple harmonic oscillator model and it arises from the time dilation due to the expansion of the Universe.
+%
+%
+%
+%\begin{wrapfigure}{r}{4cm}
 
+\begin{figure}
+\centering
+\includegraphics[scale=0.4]{baryonspring}
+\caption{Analogy between the photon-baryon fluid and the spring-mass system. (Credit: \cite{huweb})}
+\label{baryon_spring}
+\end{figure}
+%\end{wrapfigure}
+%
+%
+%
 \subsection{Acoustic Oscillations and Damping}
-\begin{wrapfigure}{r}{6cm}
-\centering
-%\begin{figure}
-\includegraphics[scale=0.5]{baryonspring}
-%\end{figure}
-\end{wrapfigure}
-Let us consider again the harmonic oscillator model in the case of $\omega_k > \gamma$, small scales where $k$ is big "enough".
+
+Let us consider the harmonic oscillator model in the case of $\omega_k > \gamma$, small scales where $k$ is big "enough".
 The respective solutions are of the form of the damped harmonic oscillator with a shift of $-gm/k$
@@
 Before recombination, the perturbations of the photon-baryon fluid behaves analogously to the damped harmonic oscillator.
-The mass that elongates the spring and falls down is analogues to the fluid falling and compressing inside a gravitational potential.\\
+The mass elongates the spring and it falls down as the photon-baryon fluid falls into a gravitational potential and it is compressed (Figure(\ref{baryon_spring})).\\
 During matter dominated era, overdensities of dark matter creates gravitational well where the photon baryon-fluid falls in.
-As a consequence the gravitational potential compresses the baryon-photon fluid and the pressure starts to rise.
+As a consequence, the gravitational potential compresses the baryon-photon fluid and the pressure starts to rise.
 Since dark matter and baryonic matter are pressureless, the system accretes until the photon pressure causes the fluid to expand outward.\\
 The process of compression and expansion gives rise to sound waves and it goes on until recombination.
+The inward and outward oscillations of the photon-baryon fluid are called acoustic oscillations, since they represent a type of standing sound wave in the photon-baryon fluid\cite{RydenIntroCosmoPdf}.\\
 Only the fluctuations that are caught at the extrema of their oscillations at recombination will become peaks in the CMB power spectrum.
@@
 The first peak of the oscillations represents the mode that compressed the fluid inside potential wells before recombination only once, the second one represents the mode that compressed and then rarefied, the third one the mode that compressed then rarefied then compressed, etc.
-exactly as a spring!
+exactly as a spring!\\
 The radiation pressure acts as a spring, whereas the inertia of the fluid as the mass of the ball.
@@
 \\
-The temperature fluctuations are damped due to collisions between the baryons and the photons that dissipate energy, and the expansion of the universe.\\
+The particles of the photon-baryon fluid experience also collisions and this leads to a damping effect on the oscillations.
+The physical scale of the damping depends on the baryon and photon density through the mean free path.
+An additional damping effect comes from the expansion of the Universe.
 %The damping scale provides another standard ruler for the curvature test
-The physical scale of the damping depends on the baryon density through the mean free path
+
 %And the matter density through the time available for the photons to random walk.
@@
 Let us now see if our predictions are compatible with the measured temperature power spectrum.
-The behavior of the primordial plasma is imprinted in the CMB photons, in fact, we observe the density fluctuations as anisotropies in the sky map tempearature.
+The behavior of the primordial plasma is imprinted in the CMB photons, in fact, we observe the density fluctuations as anisotropies in the sky map temperature.
 In order to relate the fluctuations at different scales and the deviations from the average temperature $2.7$ K on the CMB map, it is necessary to decompose the observed temperature deviation $T(\theta, \phi)$ into a set of orthonormal functions on the sky.
@@
 For large scales, small $l<30$, the power spectrum is constant and oscillations do not take place.
-Therefore, the Sachs-Wolfe effect is dominant on large scales where the oscillations have too large wavelength to complete an entire oscillations before recombination and they experience mainly the gravitational redshift.\\
+Therefore, the Sachs-Wolfe effect is dominant on large scales where the oscillations have too large wavelength to complete an entire oscillations before recombination and, consequently, the power spectrum is almost constant.\\
 For large $l$ the acoustic oscillations are dominant.
@@
 Notice that as we consider higher and higher $l$, i.e. smaller scales, the damping effects become relevant, especially for  $l>10^{3}$.\\
-
-The four density parameters $\Omega$ encode the energy-matter content of the Universe and they determine the evolution of space-time through the Friedmann equations. 
-We want now to link the information contained in the measured fluctuations of the CMB to the density parameters through the observed power spectrum.\\
+The four density parameters $\Omega$ encode the energy-matter content of the Universe and they are constrained by the shape of the CMB power spectrum.
+Since the radiation density parameter can be precisely determined by the measurements of the CMB temperature, we analyze how the power spectrum changes if we vary the other  parameters $\Omega_{k 0}$, $\Omega_{\Lambda 0}$ and $\Omega_{m 0}_$.
 
@@
 This mysterious energy that leads to the expansion of the Univers is called Dark Energy.\\
-Form Figure(\ref{DE_curv} b) we can notice that the dark energy density $\Omega_{\Lambda0}$ plays a small role in the position of the peaks. 
+From Figure(\ref{DE_curv} b) we can notice that the dark energy density $\Omega_{\Lambda0}$ plays a small role in the position of the peaks. 
 In fact, the  cosmological constant produces a small change in the distance light can travel since recombination and this influences the scale at which we measure the peaks.\\
-The position of the peaks is instead particularly sensitive to the curvature of the Universe, as show in Figure(\ref{DE_curv}a).
+The position of the peaks is instead particularly sensitive to the curvature of the Universe, as shown in Figure(\ref{DE_curv}a).
 The curvature determines how angles are deformed.
-By measuring the position of the first peak we know the angle $\theta \sim 1/l$ of the oscillations.
-By multiplying this angle and the angular distance (specifically the angular distance) we obtain the size of the oscillations for Euclidean geometry $k =0$.
-Since the first peak represents the first complete compression of the photon-baryon fluid, we can compare the size of the oscillations obtained with $k=0$ with the value obtained by multiplying the sound speed of the fluid times the time of the collapse times the expansion factor.\\
-TO BE EXPLAINED DECENTLY\\
-	Substantially the curvature and the cosmological constant do not change the shape of the acoustic peaks but they only change shift their position on the power spectrum.
+The position of the first peak is a crucial test for checking the curvature $k$ of the Universe.
+So, since the first peak represents the first complete compression of the photon-baryon fluid, we can obtain the size $S$ of the oscillations by multiplying the sound speed $c_s$ of the fluid times the time of the collapse $t_c$ times the expansion factor $a_r$: $S =c_s t_c a_r $.\\
+The size of the oscillations appear to us now at a certain angle $\theta \sim 1/l$ on the CMB sky map.
+The relation between the angle on the sky map and the size is dependent on the spatial curvature.
+So we can check if the curvature of the Universe reflect the estimated $S$.
+For instance, if the $k=0$ we can obtain the size $S$ of the oscillations by multiplying the angle $\theta \sim 1/l$ on the sky of the first peak times the angular distance $D$ to the CMB:
+$$
+\text{for } k=0 \rightarrow \qquad \theta D \mathrel{\stackon[1pt]{$=$}{$\scriptstyle?$}} c_s t_c a_r \qquad \leftarrow \text{k independent}
+$$
 
@@
 \end{center}
-\caption{$\Omega_{tot} = 1-\Omega_{k0}$}
+\caption{$\Omega_{tot} = 1-\Omega_{k0}$ and $\Omega_{DE} = \Omega_{\Lambda 0}$. (Credit: \cite{huCosmicMicrowaveBackground2001})}
 \label{DE_curv}
@@
 Baryonic matter couples to radiation through the electromagnetic interaction and it adds inertial mass to the oscillating photon-baryon fluid.
-What happens when you add mass to a spring and let it fall in the gravitational field of the Earth.  
+We have already seen what happens when you add mass to a spring and let it fall in the gravitational field of the Earth.  
 With more mass loading the spring, it falls further before pulled back by the spring. 
@@
 Therefore the oscillations will occur at smaller scales $\lambda =2 \pi /k$ and the position of the peaks is pushed to slightly higher multipoles $l$ (Figure(\ref{DM_bary})).\\
-In addition baryons influence also damping effects.\\
+%In addition baryons influence also damping effects.\\
 Radiation pressure plays the role of the spring and it is the only relevant pressure that makes expand the fluid.
@@
 Therefore, an high third peak (with respect to the first peak) is an indication of dark matter.
-In addition, having a third peak that is boosted to a height comparable to or exceeding the second peak is an indication that dark matter dominated the matter density in the plasma before recombination .
+In addition, having a third peak that is boosted to a height comparable to or exceeding the second peak is an indication that dark matter dominated the matter density in the plasma before recombination.
 
@@
 
-\begin{figure}
+\begin{figure}[h]
 \begin{center}
@@
 \end{center}
-\caption{aa}
+\caption{(Credit: \cite{huCosmicMicrowaveBackground2001})}
 \label{DM_bary}
@@
 \section{Conclusion}
+The Planck Collaboration estimated the density parameters with incredible precision:
+
+Substantially the curvature and the cosmological constant do not change the shape of the acoustic peaks but they only change shift their position on the power spectrum.
+
 The many ways that baryons show up in the power spectrum imply that the power spectrum has many independent checks on the baryon density of the universe.

### 2019-02-27 paper/main.tex
small mistake

@@
 The four density parameters $\Omega$ encode the energy-matter content of the Universe and they are constrained by the shape of the CMB power spectrum.
-Since the radiation density parameter can be precisely determined by the measurements of the CMB temperature, we analyze how the power spectrum changes if we vary the other  parameters $\Omega_{k 0}$, $\Omega_{\Lambda 0}$ and $\Omega_{m 0}_$.
+Since the radiation density parameter can be precisely determined by the measurements of the CMB temperature, we analyze how the power spectrum changes if we vary the other  parameters $\Omega _{k 0}$, $\Omega _{\Lambda 0}$ and $\Omega _{m 0}$.
 

### 2019-02-27 paper/main.tex
conclusions started

@@
 
-\caption{(NASA/COBE/DMR; NASA/WMAP SCIENCE TEAM; ESA AND THE PLANCK COLLABORATION)}
+\caption{(Credit: NASA/COBE/DMR; NASA/WMAP SCIENCE TEAM; ESA AND THE PLANCK COLLABORATION)}
 \label{cobe_wmap_planck}
@@
 \subsection{Dark Matter and Baryons}
-The matter density parameter $\Omega_{m0}$ includes any form of non-relativistic matter that interacts gravitationally, so it includes both dark matter and baryonic matter.
+The matter density parameter $\Omega_{m0}$ includes any form of non-relativistic matter that interacts gravitationally, so it includes both dark matter $\Omega_{dm}$ and baryonic matter $\Omega_{b}$.
 Baryonic matter couples to radiation through the electromagnetic interaction and it adds inertial mass to the oscillating photon-baryon fluid.
@@
 
-\section{Conclusion}
-The Planck Collaboration estimated the density parameters with incredible precision:
-
-Substantially the curvature and the cosmological constant do not change the shape of the acoustic peaks but they only change shift their position on the power spectrum.
-
+\section{Conclusions}
+The discovery of the CMB marked the beginning of a new era of cosmology.
+On one hand the challenge of precise measurements of the CMB anisotropies accelerated the technological progress.
+On the other hand the theoretical effort to build a cosmological model of the universe consistent with the observations lead to the discovery of new form of matter and energy.
+The combined results from the phenomenology of the primordial plasma with the measurements of the temperature anisotropies and other astronomical observations produced the following estimates of the density parameters:
+\begin{equation*}
+    \Omega_{b} = 0.04917 
+\qquad \Omega_{\Lambda 0} = 0.6844 \qquad \Omega_{dm} = 0.2647
+\qquad \Omega_{r0} = 8.51 \times 10^{-5} 
+\end{equation*}
+with relative errors ranging from $0.8$ \% up to $1.6$ \% and $\Omega_{k0} = 0.001 \pm 0.002$.\\
+Substantially the curvature and the cosmological constant do not change the shape of the acoustic peaks but they only change shift their position on the power spectrum.\\
 The many ways that baryons show up in the power spectrum imply that the power spectrum has many independent checks on the baryon density of the universe.  
-The baryon density is a quantity that the CMB can measure to exquisite precision.
+Therefore, the baryon density is a quantity that the CMB can measure accurately.\\
+The dark matter plays a fundamental role in shaping the CMB power spectrum and it is the main constituent of matter in our universe.
 

### 2019-02-28 paper/main.tex
conclusions

@@
 
+% changing footnotes
+\usepackage[symbol]{footmisc}
+
+\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+%\footnote[paragraph]{text}
+
+% force figures positions
+\usepackage{float}
+
 %  ---- my commands -------
@@
 Thus, the observations of the CMB fluctuations are linked to the energy-matter content of our Universe and to dark matter.\\
-The aim of this paper is to give a short and concise overview of the physics of the CMB and the cosmological evidence of Dark Matter through the analysis of the CMB fluctuations within the $\Lambda$CDM model assumptions.\\
+The aim of this paper is to give a short and concise overview of the physics of the CMB and the cosmological evidence of dark matter through the analysis of the CMB fluctuations within the $\Lambda$CDM model assumptions.\\
 We first give an historical overview of the discovery and measurements of the CMB, then we discuss the main assumptions of the $\Lambda$CDM model and the link between the energy-matter content of the Universe and the cosmological model.
@@
 In section 5 we explain how the phenomena in the primordial plasma are reflected in the measured temperature power spectrum of the CMB.
-Lastly, we discuss how the different energy-matter components influence the CMB power spectrum and we conclude that dark matter is one of the leading constituents of the universe.
+Lastly, we discuss how the different energy-matter components influence the CMB power spectrum and we conclude that dark matter is one of the leading constituents of matter present in the universe.
 
@@
 \\
-First of all, the photons of the CMB can be absorbed by the Earth's atmosphere, because the energy per CMB photon (approximately $\sim 6 \times 10 ^{-4}$ eV) is comparable to the energy of vibration or rotation for a small molecule (of water for instance).
+First of all, the CMB photons
+can be absorbed by the Earth's atmosphere, because the energy per CMB photon (approximately $\sim 6 \times 10 ^{-4}$ eV) is comparable to the energy of vibration or rotation for a small molecule (of water for instance).
 In fact, microwaves with wavelengths shorter than $\lambda \sim 3$ cm are strongly absorbed by water molecules \citep{RydenIntroCosmoPdf}.
 This problem could be overcome by observing the CMB in different bands and from locations where the atmospheric humidity is low, at high altitudes and at low temperatures.
-However, any terrestrial experiment would be able to measure only a portion of the sky map and would be affected by Earth's atmosphere, so the best way to measure the CMB spectrum is to use satellites.\\
+However, any terrestrial measurement of the CMB would be able to measure only a portion of the sky map and would be affected by Earth's atmosphere.
+Clearly, the best way to measure the CMB spectrum is to use a satellite.\\
 COBE was the first satellite launched to measure the CMB in 1989. 
@@
 COBE measured fluctuations to scales of 7$^\circ$, WMAP was able to measure resolutions down to 0.3$^\circ$ in five different frequency bands, and Planck measured all the way down to just 5 arcminutes (0.07$^\circ$) in nine different frequency bands in total.\\
-Nevertheless the satellites improved their accuracy, many other sources of noise were encountered such as the light coming from the center of our galaxy, other stars and other objects in the universe, in addition to the relative motion of the satellite with respect to the CMB (Figure (\ref{cobe_map})).\\
-Finally, observations and statistical analysis showed that the CMB spectrum is close to a black body spectrum up to fluctuations of order of $10^{-5}$ K (Figure (\ref{cobe_blackbody})).\\
+Nevertheless the satellites improved the accuracy of the measurements, many other sources of noise were encountered such as the light coming from the center of our galaxy, other stars and other objects in the universe, in addition to the relative motion of the satellite with respect to the CMB (Figure (\ref{cobe_map})).\\
+%Finally, observations and statistical analysis showed that the CMB spectrum is close to a black body spectrum up to fluctuations of order of $10^{-5}$ K (Figure (\ref{cobe_blackbody})).\\
 The technological efforts for precisely measuring the fluctuations of the CMB was a fundamental step-stone to understand what the universe is made of.
 % maybe last sentence in the introduction with the image
-
+\vspace{3cm}
 \begin{figure}[h]
 \centering
-    \textbf{Cosmic Microwave Background  Spectrum}\par\medskip
+    %\textbf{Cosmic Microwave Background  Spectrum}\par\medskip
 \centering
-   {\includegraphics[height=7cm]{blackbody}}
+   {\includegraphics[height=9cm]{blackbody}}
 \caption{The monopole spectrum of the Cosmic Microwave Background Radiation using the original data set by the FIRAS team, available at \url{http://lambda.gsfc.nasa.gov/product/cobe/firas_monopole_get.cfm}.
 The vertical axis "MJy/sr" corresponds to $10^6$ jansky per steradian, where a jansky is $10^{-26}$ Watts per square-meter per Hertz.
-The horizontal axis ("1/cm") corresponds to the reciprocal of the microwave wavelength (in cm), which is proportional to the microwave frequency.
-The error bars are too small to be displayed by a computer screen, but vastly exaggerated error bars were included to show the measured data points.}
+The horizontal axis ("1/cm") corresponds to the reciprocal of the microwave wavelength (in cm), which is proportional to the microwave frequency.}
 \label{cobe_blackbody}
@@
 \section{Energy-Matter Content of the Universe} 
-It is often said that the Universe we live in is flat and it is made up of $69$\% of Dark Energy, and $26 $\% by Dark Matter and $5$\% of ordinary matter, but what do we really mean by that?\\
+It is often said that the Universe  is flat and it is made up of $69$\% of Dark Energy, and $26 $\% by Dark Matter and $5$\% of ordinary matter, but what do we really mean by that?\\
 In this section we explain the meaning of these parameters and from which theoretical framework they come from. 
-We are going to use the assumptions of the so-called $\Lambda$CDM model.\\
+We are going to use the assumptions of the $\Lambda$CDM model.\\
 We assume that the observable properties of the Universe are isotropic and there is not a preferred direction. 
@@
 After subtracting the average temperature of the CMB from its spectrum, a moving observer with respect with the CMB will see a dipole pattern, where the blue-shifted photons come from the direction the observer is moving toward to and the red-shifted photons from the opposite direction.
-Since Earth is not at rest with respect to the CMB, the satellite COBE measured the dipole pattern showed in the second panel in Figure (\ref{cobe_map}).
-And therefore from an observer on Earth the Universe is not isotropic.
+Since Earth is not at rest with respect to the CMB, the satellite COBE measured the dipole pattern shown in the second panel in Figure(\ref{cobe_map}).
+Therefore, from an observer on Earth the Universe does not appear isotropic.
 In the following sections we consider only those observers which are at rest with respect to the Cosmic Microwave Background.\\
-In addition we assume that spacetime is described by a metric theory of gravity, and we treat spacetime as a 4-dimensional manifold characterized by the metric tensor $g_{\mu \nu}$.
+We also assume that spacetime is described by a metric theory of gravity, and we treat spacetime as a 4-dimensional manifold characterized by the metric tensor $g_{\mu \nu}$.
 The most general metric $g_{\mu \nu}$ satisfying homogeneity and isotropy assumptions is the Friedmann – Lemaître – Robertson – Walker (FLRW) metric written here in terms of the invariant geodesic distance $\dd s ^2 = g_{\mu \nu} \dd x^{\mu} \dd x^{\nu}$:
@@
 \\
-Notice that the FLRW metric has $g_{0 i}=0$ due to the isotropic assumption and the two parameters $a(t)$ and $k$ are the only allowed to preserve our assumptions, all the others parameter that we can introduce can be absorbed in these two.
+Notice that the FLRW metric has $g_{0 i}=0$ due to the isotropic assumption and the two parameters $a(t)$ and $k$ are the only allowed to preserve our assumptions, all the others parameter that we could introduce can be absorbed in these two.
 \\ % comments on the redshift, metric, what spatially flat means
@@
 In the other limit the future of the Universe is determined by the cosmological constant $\Lambda$.
-We have not specified the nature of the cosmological constant, up to now it has been treated as a possible parameter that can be added to the Einstein's field equations(\ref{einstein_eq}).
+Accordingly to the time evolution of the scale factor $a(t)$ there are different epochs in which one of the components determines the expansion rate and it is dominating over the others.
 \\
@@
 \end{equation}
-So the experimental measurements of these parameters must add up to one.
-We will see in the next sections how the CMB power spectrum puts constraints on these parameters and tell us that there is a form of matter that we cannot see in $\Omega_{m0}$.
+So the experimental measurements of these parameters must add up to one.\\
+In the next sections the CMB power spectrum will put constraints on these parameters and tell us that there is a form of matter that we cannot see in $\Omega_{m0}$.
 
 \section{Phenomenology of the Fluctuations}
-The Cosmic Microwave Background fluctuations were produced when radiation and matter were interacting in the early stage of the Universe.
-Before the release of the CMB at redshift $z > 1100$ the electromagnetic radiation is firmly coupled (both energetically and kinetically) to the baryons.
+The Cosmic Microwave Background fluctuations were produced when radiation and matter were interacting in the early stages of the Universe.
+Before the release of the CMB at redshift $z>1100$ the electromagnetic radiation is firmly coupled (both energetically and kinetically) to the baryons.
 The behavior of such a system can be studied by solving the equations of relativistic hydrodynamics and the Einstein's field equations (\ref{einstein_eq}) with small perturbations of density $\delta \rho$, pressure $\delta p$ and gravitational potential  $\delta \Phi$.
@@
 We use instead an analogy with the most favourite model of a physicist: the harmonic oscillator\footnote{As in every analogy in physics, the phenomena are not the same.
-A mass on a spring is not the same as a relativistic fluid perturbation in an expanding 4-dimensional manifold, but the analogy is very helpful for the understanding and the equations are not that different (in first approximation)}.\\
+A mass on a spring is not the same as a relativistic fluid fluctuation in an expanding 4-dimensional manifold, but the analogy is very helpful for the understanding and the equations are not that different (in first approximation)}.\\
 All kinds of perturbations are proportional to the temperature fluctuations $\Theta$, so we  can associate the fluctuations to the displacement $x$ of spring-mass system from its equilibrium.
@@
 This is called the Sachs-Wolfe effect.
-The Sachs-Wolfe effect takes into account an additional effect that cannot be explained with the simple harmonic oscillator model and it arises from the time dilation due to the expansion of the Universe.
+The Sachs-Wolfe effect takes into account an additional effect that cannot be explained with the simple harmonic oscillator model and it arises from the time dilation due to the expansion of the Universe.\\
+Thus, we expect that for large scales the temperature fluctuations are roughy constant and not oscillating.
 %
@@
 \begin{figure}
+\centering
+\textbf{Sprin-mass system}\par\medskip
 \centering
@@
 Let us now see if our predictions are compatible with the measured temperature power spectrum.
-The behavior of the primordial plasma is imprinted in the CMB photons, in fact, we observe the density fluctuations as anisotropies in the sky map temperature.
-In order to relate the fluctuations at different scales and the deviations from the average temperature $2.7$ K on the CMB map, it is necessary to decompose the observed temperature deviation $T(\theta, \phi)$ into a set of orthonormal functions on the sky.
+The the density fluctuations of the primordial plasma are imprinted in the CMB photons temperature fluctuations which we observe today as anisotropies in the temperature sky map.
+In order to relate the fluctuations at different scales and the deviations from the average temperature $2.7 \text{K}$ on the CMB map, it is necessary to decompose the observed temperature deviation $T(\theta, \phi)$ into a set of orthonormal functions on the sky.
 The spherical harmonics $Y^{m} _{l} (\theta, \phi)$ are suitable for this.\\
@@
 \centering
+\textbf{Temperature Power Spectrum}\par\medskip
+\centering
 \includegraphics[width=0.9\textwidth]{planck2018}
@@
 Since the radiation density parameter can be precisely determined by the measurements of the CMB temperature, we analyze how the power spectrum changes if we vary the other  parameters $\Omega _{k 0}$, $\Omega _{\Lambda 0}$ and $\Omega _{m 0}$.
-
+\vspace{2cm}
+\begin{figure}[H]
+\centering
+\textbf{Temperature Power Spectrum with varying Curvature and Dark Energy density parameters}
+\begin{center}
+\includegraphics[width=\textwidth]{curvature_de}
+\end{center}
+\caption{$\Omega_{tot} = 1-\Omega_{k0}$ and $\Omega_{DE} = \Omega_{\Lambda 0}$. (Credit: \cite{huCosmicMicrowaveBackground2001})}
+\label{DE_curv}
+\end{figure}
 \subsection{Dark Energy and Curvature}
@@
 This mysterious energy that leads to the expansion of the Univers is called Dark Energy.\\
-From Figure(\ref{DE_curv} b) we can notice that the dark energy density $\Omega_{\Lambda0}$ plays a small role in the position of the peaks. 
+From Figure(\ref{DE_curv} b) it is evident that the dark energy density $\Omega_{\Lambda0}$ plays a small role in the position of the peaks. 
 In fact, the  cosmological constant produces a small change in the distance light can travel since recombination and this influences the scale at which we measure the peaks.\\
@@
 The size of the oscillations appear to us now at a certain angle $\theta \sim 1/l$ on the CMB sky map.
+From Figure(\ref{temp_pow_spect}) the size of the first compression is located at $l\approx200 \rightarrow \theta \approx 1^\circ$.
 The relation between the angle on the sky map and the size is dependent on the spatial curvature.
@@
 $$
-
+%Substantially the curvature and the cosmological constant do not change the shape of the acoustic peaks but they only change shift their position on the power spectrum.\\
+%
+%
 % Given our current uncertainties about the physical density of the matter, the distance that sound can travel by recombination is currently uncertain, a fact related to the matter's effect on the age of the universe at recombination.
@@
 As it turns out, the sound horizon is not a standard ruler but rather a standardizeable ruler.
-\begin{figure}
-\begin{center}
-\includegraphics[width=\textwidth]{curvature_de}
-\end{center}
-\caption{$\Omega_{tot} = 1-\Omega_{k0}$ and $\Omega_{DE} = \Omega_{\Lambda 0}$. (Credit: \cite{huCosmicMicrowaveBackground2001})}
-\label{DE_curv}
-\end{figure}
 
@@
 More baryons would enhance the odd peaks and suppress the even ones as shown in Figure(\ref{DM_bary}a).\\
+\begin{figure}[H]
+\centering
+\textbf{Temperature Power Spectrum with varying Baryon and Matter density parameters}\par\medskip
+\begin{center}
+\includegraphics[width=\textwidth]{baryon_m}
+\end{center}
+\caption{Panel(a) shows how the power spectrum changes according to the amount of baryons.
+Panel(b) shows how the matter density parameter affects the temperature power spectrum by keeping constant the baryonic content, it basically shows the effect of dark matter.
+(Credit: \cite{huCosmicMicrowaveBackground2001})}
+\label{DM_bary}
+\end{figure}
+\pagebreak
 Increasing the mass of the spring would decrease the oscillations of the spring $\omega_k = \sqrt{k/m}$.
@@
 Therefore the oscillations will occur at smaller scales $\lambda =2 \pi /k$ and the position of the peaks is pushed to slightly higher multipoles $l$ (Figure(\ref{DM_bary})).\\
+%
 %In addition baryons influence also damping effects.\\
@@
 On the other hand, raising the dark matter density reduces the overall amplitude of the peaks.
-
 The third peak is linked to a cycle of compression rarefaction and again compression of the fluid.
@@
 
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=\textwidth]{baryon_m}
-\end{center}
-\caption{(Credit: \cite{huCosmicMicrowaveBackground2001})}
-\label{DM_bary}
-\end{figure}
-
 \section{Conclusions}
@@
 On one hand the challenge of precise measurements of the CMB anisotropies accelerated the technological progress.
-On the other hand the theoretical effort to build a cosmological model of the universe consistent with the observations lead to the discovery of new form of matter and energy.
+On the other hand the theoretical effort to build a cosmological model of the universe consistent with the observations lead to the discovery of new form of matter and energy.\\
+We have seen that Dark Energy and the curvature do not affect the shape of the temperature power spectrum but they only shift the peaks.\\
+The many ways that baryons show up in the power spectrum imply that the power spectrum has many independent checks on the baryon density of the universe \cite{huweb}.  
+Therefore, the baryon density is a quantity that the CMB can measure accurately.\\
+The dark matter plays a fundamental role in shaping the CMB power spectrum and it is the main constituent of matter in our universe.\\
 The combined results from the phenomenology of the primordial plasma with the measurements of the temperature anisotropies and other astronomical observations produced the following estimates of the density parameters:
@@
 with relative errors ranging from $0.8$ \% up to $1.6$ \% and $\Omega_{k0} = 0.001 \pm 0.002$.\\
-Substantially the curvature and the cosmological constant do not change the shape of the acoustic peaks but they only change shift their position on the power spectrum.\\
-The many ways that baryons show up in the power spectrum imply that the power spectrum has many independent checks on the baryon density of the universe.  
-Therefore, the baryon density is a quantity that the CMB can measure accurately.\\
-The dark matter plays a fundamental role in shaping the CMB power spectrum and it is the main constituent of matter in our universe.
+It is evident from these parameters that we live in a spatially flat Universe mostly governed by Dark Energy.\\
+In addition, dark matter is the dominant form of matter that constitutes the Universe.
 

### 2019-02-28 paper/main.tex
pdf produced

--- 2019-02-27 paper/main.tex
@@
 \section{Conclusion}
+The discovery of the CMB marked the beginning of a new era of cosmology.
+On one hand the challenge of precise measurements of the CMB anisotropies accelerated the technological progress.
+On the other hand the theoretical effort to build a cosmological model of the universe consistent with the observations lead to the discovery of new form of matter and energy.
+The combined results from the phenomenology of the primordial plasma with the measurements of the temperature anisotropies and other astronomical observations produced the following estimates of the density parameters:
+\begin{equation*}
+    \Omega_{b} = 0.04917 
+\qquad \Omega_{\Lambda 0} = 0.6844 \qquad \Omega_{dm} = 0.2647 \qquad \Omega_{k0} = 0
+\qquad \Omega_{r0} = 8.51 \times 10^{-5} 
+\end{equation*}
+
+Substantially the curvature and the cosmological constant do not change the shape of the acoustic peaks but they only change shift their position on the power spectrum.
+
+The many ways that baryons show up in the power spectrum imply that the power spectrum has many independent checks on the baryon density of the universe.
+The baryon density is a quantity that the CMB can measure to exquisite precision.
+
 The Planck Collaboration estimated the density parameters with incredible precision:

### 2019-02-28 paper/main.tex
restore old commit

--- 2019-02-28 paper/main.tex
@@
 with relative errors ranging from $0.8$ \% up to $1.6$ \% and $\Omega_{k0} = 0.001 \pm 0.002$.\\
-It is evident from these parameters that we live in a spatially flat Universe mostly governed by Dark Energy.\\
+The density parameters are estimated with an astonishing precision and they reveal the true content of the Universe.
+It is evident from these parameters that we live in a spatially flat Universe mostly governed by Dark Energy, which is the source of the accelerated expansion.\\
 In addition, dark matter is the dominant form of matter that constitutes the Universe.
+Dark matter plays a fundamental role in the early stages of the Universe through his gravitational interaction and it is the seed for the formation of structures in the Universe.
+And the Cosmic Microwave Background gives one of the most compelling evidence of the existence of this new form of matter by using the best theory of gravity that we know: the General Theory of Relativity.
+\pagebreak
 

### 2019-02-28 paper/main.tex
Updates from Overleaf

--- 2019-02-28 paper/main.tex
@@
 \section{Introduction}
-Many astronomical and cosmological observations suggest that, by using the General Theory of Relativity, there is an invisible form of matter that exerts a gravitational pull on baryonic matter. 
+Many astronomical and cosmological observations suggest that, by using the General Theory of Relativity, there is an invisible form of matter that exerts a gravitational pull on baryons. 
 In order to explain such observations, scientists have proposed the existence of Dark Matter, a new form of matter that does not interact electromagnetically and, therefore, it appears invisible to us.

### 2019-02-28 paper/main.tex
final version

--- 2019-02-28 paper/main.tex
@@
 In order to explain such observations, scientists have proposed the existence of Dark Matter, a new form of matter that does not interact electromagnetically and, therefore, it appears invisible to us.
-The fundamental nature of Dark Matter is not well understood yet, and whether Dark Matter is truly a new form of matter or the consequence of new laws of gravity is still matter of debate.\\
+The fundamental nature of Dark Matter is not well understood yet, and whether Dark Matter is truly a new form of matter or the consequence of new laws of gravity is still an open debate.\\
 One of the most compelling evidence for the existence of Dark Matter is given by the analysis of the Cosmic Microwave Background (CMB).\\
